\chapter{Mi'ihen Highroad}

\begin{enumerate}
	\item Walk up. Forced encounter, \sd. Walk up, \sd\ during Maechen Scene. Guaranteed 1 Power Sphere from the tutorial.
\end{enumerate}
\begin{encounters}
	\begin{itemize}
		\item Bomb:
		      \begin{itemize}
			      \switch{anyone}{\kimahri}
			      \kimahrif Lancet Bomb, learn \textbf{Self Destruct}
			      \item Flee.
		      \end{itemize}
		\item Else Flee,  Heal afterwards if it was an ambush.
	\end{itemize}
\end{encounters}
\begin{enumerate}[resume]
	\item {Mi'ihen Skip}
	      \begin{itemize}
		      \item After Maechen Scene, run up as quickly as possible.
		      \item Go to the White Spot on the ground towards the left before the Man in Blue
		      \item Speak to the man, get the \textbf{Hunter's Spear}
		      \item Mash and step forward over the cutscene line
		      \item Walk up during the cutscene after the teleport to the next screen.
	      \end{itemize}
	\item Make sure you get the \textbf{Hunter's Spear} if you fail the skip.
	\item Go right and \sd\ at Calli scene. Continue walking up. \sd\ Luzzu scene, \sd\ Shelinda scene
	\item \formation{\tidus}{\wakka}{\kimahri}
	\item Go to the next screen
	\item Go to the Al-Bhed shop, \sd. Walk out of the shop and \cs[5:30]
	\item Leave shop, \sd. \sd\ on Rin. Walk outside.
\end{enumerate}
\begin{battle}{Chocobo Eater}
	\begin{itemize}
		\tidusf Haste Boss
		\item Defend with everyone.
		\item Swap any characters that fall into crit HP with someone in the back.
	\end{itemize}
\end{battle}
\begin{enumerate}[resume]
	\item \sd
	\item Walk north, \save. Walk north to next screen. Walk to blocked road, \sd. Speak to the guard on the right, \sd, walk back, \sd. Walk up to next screen.
	\item \textit{If you don't have \textbf{Self Destruct}, make sure that you get it before leaving the second screen.}
\end{enumerate}
\newpage