\chapter{Taejin's Tower}

Activate Mission 20.

\begin{menu}
	\begin{itemize}
		\equip
		\begin{itemize}
			\item Sazh
				\begin{itemize}
					\item Sorcerer's Mark*
					\item Shaman's Mark Lv.1
				\end{itemize}
			\item Lightning ($\leftarrow$)
				\begin{itemize}
					\item Unequip everything
				\end{itemize}
			\item Fang ($\leftarrow$)
				\begin{itemize}
					\item Unequip everything
				\end{itemize}
		\end{itemize}
	\end{itemize}
\end{menu}

Use a \textbf{Deceptisol} before engaging Mission 20.

\begin{battle}{{Mission 20: Goblin Chieftain, Goblin x2, Munchkin Maestro \& Munchkin -- Pre-Empt}}
	\begin{itemize}
		\item \third
			\begin{itemize}
				\item Quake
				\item Auto-Support twice
				\item Faith-Enfire Sazh
			\end{itemize}
		\item \fifth
			\begin{itemize}
				\item Quake
				\item Fira-Fira on small enemies, \com-buffer into [1]
			\end{itemize}
		\item \first
			\begin{itemize}
				\item Immediately shift
			\end{itemize}
		\item \fifth
			\begin{itemize}
				\item Fira-Fira, \com-buffer into [1]
				\item Repeat loop until victory
			\end{itemize}
	\end{itemize}
\end{battle}

Pick up the \textbf{Sinister Fang x20} chest after the fight.
Make your way into the tower and use the elevator to get to the Second Tier.

\begin{menu}
	\begin{itemize}
		\paradigm
		\begin{itemize}
			\item \paradigmdeck{%
				      \paradigmline{Sazh}{Vanille}{Snow}}%
				  {\paradigmline{(\syn)}{\sab}{(\com)}}%
			      {\paradigmline{\com}{\rav}{\rav}}%
			      {\paradigmline[4]{\syn}{(\sab)}{(\rav)}}%
			      {\paradigmline{\com}{(\rav)}{\com}}%
			      {\paradigmline{\rav}{\sab}{(\rav)}}%
			      {\paradigmline{\com}{\med}{\com}}%			      			    
		\end{itemize}
		\equip
		\begin{itemize}
			\item Sazh
				\begin{itemize}
					\item Power Wristband*
					\item Warrior's Wristband Lv.8
				\end{itemize}
			\item Vanille ($\rightarrow$)
				\begin{itemize}
					\item Black Belt*
					\item Shield Talisman Lv.1
				\end{itemize}
		\end{itemize}
	\end{itemize}
\end{menu}

\renewcommand{\first}{[1] Bully (\syn/\sab/\com)}
\renewcommand{\second}{[2] Relentless Assault (\com/\rav/\rav)}
\renewcommand{\third}{[3] Guerilla (\syn/\sab/\rav)}
\renewcommand{\fourth}{[4] Aggression (\com/\rav/\com)}
\renewcommand{\fifth}{[5] Smart Bomb (\rav/\sab/\rav)}
\renewcommand{\sixth}{[6] Tireless Charge (\com/\med/\com)}

Accept Mission 21 and pre-empt Gelatitan.

\begin{battle}{Mission 21: Gelatitan -- Pre-Empt}
	\begin{itemize}
		\item Any\% strat
	\end{itemize}
\end{battle}

Activate Mission 22.

\begin{menu}
	\begin{itemize}
		\paradigm
		\begin{itemize}
			\item Default [2]
			\item Battle Team
				\begin{itemize}
					\item Swap Sazh with Vanille (1 $\leftrightarrow$ 2)
				\end{itemize}						      			      	
		\end{itemize}
	\end{itemize}
\end{menu}

Use an \textbf{Ethersol} and pre-empt Ambling Bellows.

\begin{battle}{Mission 22: Ambling Bellows -- Pre-Empt}
	\begin{itemize}
		\item Any\% strat
	\end{itemize}
\end{battle}

Activate Mission 23.

\begin{menu}
	\begin{itemize}
		\paradigm
		\begin{itemize}
			\item Default [3]
			\item Battle Team
				\begin{itemize}
					\item Swap Vanille with Sazh (1 $\leftrightarrow$ 2)
				\end{itemize}						      			      	
		\end{itemize}
	\end{itemize}
\end{menu}

Pre-empt Gurangatch.

\begin{battle}{Mission 23: Ambling Bellows -- Pre-Empt}
	\begin{itemize}
		\item Any\% strat
	\end{itemize}
\end{battle}

Pick up the \textbf{Simurgh} chest.
Activate Mission 24 and pre-empt it.

\begin{battle}{Mission 24: Mushussu -- Pre-Empt}
	\begin{itemize}
		\item Any\% strat
	\end{itemize}
\end{battle}

\begin{menu}
	\begin{itemize}
		\crystarium
		\begin{itemize}
			\item Sazh
				\begin{itemize}
					\item \rav
						\begin{itemize}
							\item 17 nodes, up 2 (Firaga)
						\end{itemize}
				\end{itemize}
			\item Vanille
				\begin{itemize}
					\item \rav
						\begin{itemize}
							\item 10 nodes, right 2 (Blizzara)
						\end{itemize}
					\item \sab
						\begin{itemize}
							\item 13 nodes, right 2 (Deprotega)
							\item 2 nodes, left 1 (Jinx)
						\end{itemize}
					\item \med
						\begin{itemize}
							\item back 1, left 2 (HP+100 x2)
							\item 1 node, down 3 (Curasa)
						\end{itemize}
				\end{itemize}
			\item Snow
				\begin{itemize}
					\item \sen
						\begin{itemize}
							\item 13 nodes (Strength+18)
						\end{itemize}
				\end{itemize}							      	
		\end{itemize}
		\equip
		\begin{itemize}
			\item Sazh
				\begin{itemize}
					\item Power Wristband* $\rightarrow$ Platinum Bangle Lv.1
				\end{itemize}
			\item Vanille ($\rightarrow$)
				\begin{itemize}
					\item Shield Talisman Lv.1 $\rightarrow$ Mythril Bangle Lv.1
				\end{itemize}
		\end{itemize}
	\end{itemize}
\end{menu}

Activate Mission 25.
Pick up the \textbf{Unsetting Sun}.

\begin{battle}{Mission 25: Vetala}
	\begin{itemize}
		\item Any\% strat
	\end{itemize}
\end{battle}

Pick up the \textbf{Librascope}.

Activate Mission 26 and use a \textbf{Deceptisol} to pre-empt it.

\begin{menu}
	\begin{itemize}
		\paradigm
		\begin{itemize}
			\item Battle Team
				\begin{itemize}
					\item Swap Vanille with Snow (2 $\leftrightarrow$ 3)
				\end{itemize}
			\item \paradigmdeck{%
				      \paradigmline{Sazh}{Snow}{Vanille}}%
				  {\paradigmline{\syn}{(\sen)}{(\rav)}}%
			      {\paradigmline[4]{\com}{\rav}{\rav}}%
			      {\paradigmline{(\rav)}{(\sen)}{(\rav)}}%
			      {\paradigmline{\com}{\com}{\rav}}%
			      {\paradigmline{\rav}{(\sen)}{\sab}}%
			      {\paradigmline{\com}{\com}{(\rav)}}%				      			     
		\end{itemize}
		\equip
		\begin{itemize}
			\item Sazh
				\begin{itemize}
					\item Warrior's Wristband Lv.8 $\rightarrow$ Sorcerer's Mark*
				\end{itemize}
		\end{itemize}
	\end{itemize}
\end{menu}

\renewcommand{\first}{[1] Riot Shield (\syn/\sen/\rav)}
\renewcommand{\third}{[3] Mystic Tower (\rav/\sen/\rav)}
\renewcommand{\fourth}{[4] Aggression (\com/\com/\rav)}
\renewcommand{\fifth}{[5] Matador (\rav/\sen/\sab)}
\renewcommand{\sixth}{[6] Aggression (\com/\com/\rav)}

\begin{battle}{Mission 26: Penanggalan -- Pre-Empt}
	\begin{itemize}
		\item \second
			\begin{itemize}
				\item Quake
				\item Target Penanggalan ($\uparrow\uparrow$)
				\item Shift immediately
			\end{itemize}
		\item \third
			\begin{itemize}
				\item Firaga
				\item Repeat, \com-buffer into [4]
			\end{itemize}
		\item \fourth
			\begin{itemize}
				\item Ruin x4
			\end{itemize}
		\item \third
			\begin{itemize}
				\item Repeat, \com-buffer into [4]
			\end{itemize}
		\item \fourth
			\begin{itemize}
				\item Repeat until victory
			\end{itemize}
	\end{itemize}
\end{battle}

\begin{upgrade}
	\begin{itemize}
		\item Upgrade
			\begin{itemize}
				\item Accesories
					\begin{itemize}
						\item Warrior's Wristband Lv.1
							\begin{itemize}
								\item Sinister Fang x10
								\item Sinister Fang all
								\item Particle Accelerator x3
							\end{itemize}
					\end{itemize}
			\end{itemize}
	\end{itemize}
\end{upgrade}

\begin{menu}
	\begin{itemize}
		\item Equipment
			\begin{itemize}
				\item Sazh
					\begin{itemize}
						\item Warrior's Wristband*
						\item Warrior's Wristband Lv.8
					\end{itemize}
				\item Vanille ($\rightarrow\rightarrow$)
					\begin{itemize}
						\item Diamond Bangle Lv.1
						\item Sorcerer's Mark*
					\end{itemize}
			\end{itemize}
	\end{itemize}
\end{menu}

Use an \textbf{Ethersol} before Dahaka.

\begin{battle}{Dahaka}
	\begin{itemize}
		\item Any\% strat
	\end{itemize}
\end{battle}

Activate the statue at the Apex (opposite to the Oerba elevator).
Use the elevator to access the Seventh Tier.
Activate the statue there (Deceptisol to dodge the birds) and pick up the \textbf{Collector Catalog}.
Use the central elevator to get back to the Apex.
Pick up \textbf{Ethersol} near the Oerba elevator.

\begin{menu}
	\begin{itemize}
		\paradigm
		\begin{itemize}
			\item \paradigmdeck{%
				      \paradigmline{Sazh}{Snow}{Vanille}}%
				  {\paradigmline{\syn}{(\rav)}{(\sab)}}%
			      {\paradigmline{\com}{\rav}{\rav}}%
			      {\paradigmline[4]{\rav}{\sen}{(\med)}}%
			      {\paradigmline{\com}{(\sen)}{(\med)}}%
			      {\paradigmline{\rav}{(\rav)}{\sab}}%
			      {\paradigmline{\com}{(\rav)}{(\med)}}%				      		
		\end{itemize}
		\crystarium
		\begin{itemize}
			\item Sazh
				\begin{itemize}
					\item \rav
						\begin{itemize}
							\item 6 nodes (HP+100)
						\end{itemize}
				\end{itemize}
			\item Snow
				\begin{itemize}
					\item \com
						\begin{itemize}
							\item 2 nodes, right 2 (Scourge)
							\item 15 nodes (Strength+18)
						\end{itemize}
					\item \sen
						\begin{itemize}
							\item 2 nodes (ATB Segment)
						\end{itemize}
				\end{itemize}
			\item Vanille
				\begin{itemize}
					\item \med
						\begin{itemize}
							\item 5 nodes, right 2 (Accesory)
						\end{itemize}
				\end{itemize}							      	
		\end{itemize}
		\equip
		\begin{itemize}
			\item Sazh
				\begin{itemize}
					\item Sorcerer's Mark Lv.1
					\item Tetradic Tiara Lv.1
				\end{itemize}
			\item Snow ($\rightarrow$)
				\begin{itemize}
					\item Black Belt*
					\item Shield Talisman Lv.1
				\end{itemize}
			\item Vanille ($\rightarrow$)
				\begin{itemize}
					\item Diamond Bangle Lv.1 $\rightarrow$ Mythril Bangle Lv.1
					\item Blank $\rightarrow$ Shaman's Mark Lv.1
				\end{itemize}
		\end{itemize}
	\end{itemize}
\end{menu}