\chapter{Academia 500F}

\begin{shop}{60000}
	\begin{itemize}
		\item Sell:
		      \begin{itemize}
			      \item Accessories:
			            \begin{itemize}
				            \item All but \textit{Grimoire Hat}
			            \end{itemize}
			      \item Components:
			            \begin{itemize}
				            \item First Slot
				            \item Tears of Remorse
				            \item Gold Nuggets
				            \item Any Expensive Monster Materials \textit{Except Essences, Crystals, and Orbs}
			            \end{itemize}
		      \end{itemize}
		\item Buy:
		      \begin{itemize}
			      \item Monster Materials:
			            \begin{itemize}
				            \item 16 Power Orbs
				            \item 32 Power Essences
			            \end{itemize}
			      \item Items
			            \begin{itemize}
				            \item 21 Potions
			            \end{itemize}
		      \end{itemize}
	\end{itemize}
\end{shop}
\begin{menu}
	\begin{itemize}
		\crystarium
		\begin{itemize}
			\item Noel
			      \begin{itemize}
				      \item \sen\ Level 40
				      \item \stagebonus{Reprieve}
				      \item \stagebonus{ACC Slot}
			      \end{itemize}
			\item \chu
			      \begin{itemize}
				      \item If you only have 6 Potent Orbs, use them
				      \item Power Orbs
				      \item \stagebonus{ATB}
				      \item Vitality Essences
				      \item Power Essences
			      \end{itemize}
		\end{itemize}
		\equip
		\begin{itemize}
			\item Noel: Grimoire Hat
		\end{itemize}
	\item Change Leader to Noel
	\end{itemize}
\end{menu}

Go Left first, then turn Right towards the L-Block. Turn Right and jump onto the next L-Block.

\begin{battle}{Pacos Amethys and Pacos Luvulite}
	\begin{flushleft}
		\begin{itemize}
			\item \sixth
			      \begin{itemize}
				      \item Switch Target to Amethyst
				      \item Librascope
				      \item Flamestrike x5
			      \end{itemize}
			\item \third
			      \begin{itemize}
				      \item Repeat
				      \item Potion as needed
				      \item Shift after Serah finishes her second chain on Luvulite
			      \end{itemize}
			\item \fifth
			      \begin{itemize}
				      \item Repeat, ATB refresh with [6] until Amethyst dies
				      \item Blizzard x5
				      \item Hope that either Serah or Noel dies, Potion \chu\ to keep him in green hp
				      \item Blizzara-Blizzaga when Split Starts
				      \item Repeat and refresh with [6] until end
			      \end{itemize}
		\end{itemize}
	\end{flushleft}
\end{battle}

Turn around and examine the switch. Turn Left, wait for the L-Block. Run back utnil the next switch, run back to the next L-Block. \throw{Shaman's Mark}{on the other platform}

Once the L-Block rotates, go to the other side, then head east. Halfway through the long walk use the Cactuar. Once the T-Block faces north or west, use the switch. Jump on the T-Block and onto the stairs.

Jump on the stationary L-Block, then go for the next T-Block.

Go onto the next platform and waitf or the next T-Block. \throw{7 Vitality Boosters}{somewhere if your Gil is low}

Jump onto the next T-Block. If you got 2 Scarletites, wait for it to rotate twice, otherwise only once. Run up the stairs to the L-block and jump to stay on it when it turns.

After it's finished rotating, go to the new way and \throw{8 Mana Essences Chest}{on the platform}

Run to the other end of the L-block and make the jump to the L-block below.

\begin{battle}{Apkallu PRE-EMPT}
	\begin{flushleft}
		\begin{itemize}
			\item \sixth
			      \begin{itemize}
				      \item Thunder x5
			      \end{itemize}
			\item \fifth
			      \begin{itemize}
				      \item Repeat x2
			      \end{itemize}
		\end{itemize}
	\end{flushleft}
\end{battle}

Examine the switch. Run back to the L-block. Jump back to the T-block and go north. Turn Left and wait for the L-block to rotate. Go up the last set of stairs.

\begin{shop}{41000}
	\begin{itemize}
		\item Sell:
		      \begin{itemize}
			      \item Everything but Power Essences and Potent Crystals
		      \end{itemize}
		\item Buy:
		      \begin{itemize}
			      \item 21 Power Essences
		      \end{itemize}
	\end{itemize}
\end{shop}
\begin{menu}
	\begin{itemize}
		\crystarium
		\begin{itemize}
			\item \chu
			      \begin{itemize}
				      \item All Power Essences
				      \item \stagebonus{ATB Segment}
				      \item All Potent Crystals
			      \end{itemize}
		\end{itemize}
	\end{itemize}
\end{menu}

\begin{battle}{Chaos Bahamut 3}
	\begin{flushleft}
		\begin{itemize}
			\item \sixth
			      \begin{itemize}
				      \item Auto-chain
				      \item Shift after second swipe
			      \end{itemize}
			\item \second
			      \begin{itemize}
				      \item Auto-chain
				      \item Feral Link \circlec, \squarec, \circlec
			      \end{itemize}
			\item \sixth
			      \begin{itemize}
				      \item Potion
				      \item Auto-chain, refresh with [6] until Megaflare
			      \end{itemize}
			\item \fourth
			      \begin{itemize}
				      \item Tank Megaflare
				      \item Potion
			      \end{itemize}
			\item \fifth
			      \begin{itemize}
				      \item Potion if \chu\ is not in green hp
				      \item Repeat, refresh with [6] until dead
			      \end{itemize}
		\end{itemize}
	\end{flushleft}
\end{battle}

\begin{battle}{Deck Caius}
	\begin{flushleft}
		\begin{itemize}
			\item \sixth
			      \begin{itemize}
				      \item Auto-chain
			      \end{itemize}
			\item \fifth
			      \begin{itemize}
				      \item Auto-chain
				      \item Fire-Thunder-Fire-Thunder
			      \end{itemize}
			\item \sixth
			      \begin{itemize}
				      \item Repeat
			      \end{itemize}
		\end{itemize}
	\end{flushleft}
\end{battle}

\begin{battle}{Beach Caius}
	\begin{flushleft}
		\begin{itemize}
			\item \sixth
			      \begin{itemize}
				      \item Aerora-Aero-Aerora, execute after Serah starts chaining
			      \end{itemize}
			\item \fifth
			      \begin{itemize}
				      \item Aerora-Aero
			      \end{itemize}
			\item \fourth
			      \begin{itemize}
				      \item Shift once Serah Provokes
			      \end{itemize}
			\item \fifth
			      \begin{itemize}
				      \item \stagger\ once Serah is about to die or is dead
				      \item Aerora-Aero-Aerora
			      \end{itemize}
			\item \sixth
			      \begin{itemize}
				      \item Repeat
			      \end{itemize}
		\end{itemize}
	\end{flushleft}
\end{battle}

\begin{battle}{Final Bahamut}
	\begin{flushleft}
		\begin{itemize}
			\item \sixth
			      \begin{itemize}
				      \item Librascope
			      \end{itemize}
			\item \fifth
			      \begin{itemize}
				      \item Auto-chain Garnet
			      \end{itemize}
			\item \third
			      \begin{itemize}
				      \item Auto-chain
			      \end{itemize}
			\item \fifth
			      \begin{itemize}
				      \item Auto-chain
				      \item Potion
				      \item Auto-chain, refresh with [6] until Garnet dies
				      \item Fire-Thunder-Fire-Thunder-Fire on Amber
			      \end{itemize}
			\item \third
			      \begin{itemize}
				      \item Repeat
			      \end{itemize}
			\item \fifth
			      \begin{itemize}
				      \item Repeat until Amber dies
				      \item Make sure that you're at almost full HP
				      \item Unicorn Horn after Break Curse
				      \item Repeat
				      \item Shift after the First Dark Flame
			      \end{itemize}
			\item \second
			      \begin{itemize}
				      \item Repeat
				      \item Feral Link
				      \item Potion
			      \end{itemize}
			\item \sixth
			      \begin{itemize}
				      \item Repeat
			      \end{itemize}
			\item \third
			      \begin{itemize}
				      \item Repeat until Deprotect
			      \end{itemize}
			\item \fifth
			      \begin{itemize}
				      \item Hope that Serah died
				      \item Aerora-Aero-Aerora, repeat with [6] until dead
				      \item If he uses any more moves, tank in \fourth
			      \end{itemize}
		\end{itemize}
	\end{flushleft}
\end{battle}

