\chapter[Chapter 1]{}
\begin{multicols}{2}
\begin{battle}{Manasvin Warmech (1)}
\end{battle}

Camera Trick for the first dodge, stick by the right for the second.

\begin{battle}{Pantheron \& PSICOM Warden}
\end{battle}

Camera Trick on the ramp and hope Sazh is nice.

\begin{battle}{PSICOM Marauder \& PSICOM Enforcer x2}
\itemdrop{19}{Phoenix Down}
\end{battle}

Legendary Dodge - Camera trick immediately. Hopefully the dogs hold short and you can run to the right around them.

\begin{battle}{Legendary Dodge - Pantheron x2 \& PSICOM Warden x2}
\begin{itemize}
    \item Hand Grenade PSICOM Warden A
    \item Repeat PSICOM Warden B
    \item Repeat Pantheron A
    \item Hand Grenade + Auto Battle if anyone is left alive
\end{itemize}

\itemdrop{19}{Phoenix Down}
\end{battle}

Camera trick after the first dodge in the Beta Behemoth hallway.

\begin{battle}{Beta Behemoth}
\begin{itemize}
    \item Throw a potion to prevent Snow's interruption by the swipe.
    \item Auto-battle twice
    \item Auto-battle and execute at 1.5 ATB, should dodge swipe
    \item Auto-battle twice
    \item Auto-battle, execute at 1.9 ATB, should dodge swipe
    \item Auto-battle until victory
\end{itemize}
\end{battle}

\save{1}

\begin{battle}{Myrmidon}
\begin{itemize}
    \item Auto battle and execute at 1.5 ATB
    \item Auto-battle
    \item Auto-battle 1 Attack
    \item Auto-battle and execute at 1.5 ATB
    \item Auto-battle
    \item Throw a potion at any point if anyone goes to less than 60hp
    \item Auto-battle once staggered, try to interrupt.
\end{itemize}

\itemdrop{25}{Polymer Emulsion}
\end{battle}

\pickup{Power Circle}{in front}

\begin{menu}
\begin{itemize}
    \item \textbf{Equipment}
    \begin{itemize}
        \item Snow
        \begin{itemize}
            \item Optimize: Offensive (Power Circle)
        \end{itemize}
    \end{itemize}
\end{itemize}
\end{menu}

Run through and fight if you fail it.

\begin{battle}{Pantheron x2 \& PSICOM Aerial Recon x3}
\begin{itemize}
    \item Hand Grenade whatever PSICOM Aerial Recon will hit the most things. Swap targets after every one to change Gadot's damage.
    \item Hand Grenades until the last thing left is not at full hp.
\end{itemize}

\itemdrop{27.1}{Phoenix Down}
\end{battle}

\begin{battle}{PSICOM Warden \& PSICOM Enforcer x2}
\itemdrop{27.1}{Phoenix Down}
\end{battle}

\save{1}
\end{multicols}
