\chapter[Chapter 2]{}

\begin{multicols}{2}
\begin{battle}{Pantheron}
\begin{itemize}
    \item Attack x2
    \item Repeat
\end{itemize}
\end{battle}

The following two fights can turn into 100\% decepts by setting battle speed to slow and waiting 23 seconds. Do this for {\bf PW Skip}
\begin{battle}{Zwerg Scandroid x3 (1)}
\itemdrop{50}{Deceptisol}
\end{battle}

\begin{battle}{Zwerg Scandroid x3 (2)}
\itemdrop{50}{Deceptisol}
\end{battle}

\begin{battle}{Pantheron x2}
\begin{itemize}
    \item Hand Grenade x3, Attack x2 if not dead
    \item Target nearest Pantheron while ATB is charging, then switch to rear Pantheron for Grenade
\end{itemize}
\itemdrop{12}{Fortisol}
\end{battle}

Camera trick the dogs after prompt. Fight the Scandroids if you need Phoenix Down and you want/need Deceps.

\begin{battle}{Zwerg Scandroid x4 (Lightning Lead)}
\begin{itemize}
    \item Attack after 32 seconds have passed. Should be when Sazh attacks the last one remaining, also go by audio cue.
\end{itemize}
\itemdrop{96}{Deceptisol} if got the 0 stars
\end{battle}

\pickup{Phoenix Down}{after the scandroids}

\begin{battle}{Pantheron \& Zwerg Scandroid x2 (Lighting Lead)}
\itemdrop{12}{Fortisol}
\end{battle}

\pickup{Gladius}{after the Pantheron}

\begin{battle}{Pantheron \& Zwerg Scandroid x2 (Snow Lead)}
\itemdrop{12}{Deceptisol}
\end{battle}
Access the menu in mid-air.

\begin{menu}
\begin{itemize}
    \item \textbf{Settings}
    \begin{itemize}
        \item Battle Speed: Slow
    \end{itemize}
\end{itemize}
\end{menu}

\begin{battle}{Zwerg Scandroid x4 (Vanille Lead) \textbf{Don't Pre-Empt}}
\begin{itemize}
    \item Attack x1
    \item Wait 32 seconds or let Hope end the fight.
\end{itemize}
\itemdrop{96}{Fortisol}
\end{battle}

\pickup{Fortisol}{ beind the Scandroids}
\begin{menu}
\begin{itemize}
    \item \textbf{Settings}
    \begin{itemize}
        \item Battle Speed: Normal
    \end{itemize}
\end{itemize}
\end{menu}

\begin{battle}{Ghoul x3}
\itemdrop{12}{Fortisol}
\end{battle}

Optional fight/chest. Menu changes for skipping this will be denoted with {\bf PW Skip}.
\begin{battle}{Ghoul x2 \textbf{Pre-Empt}}
\begin{itemize}
    \item Blitz if both are close, Attack x2 otherwise
    \item If Attack x2, change targets after Sazh hits one of them to stagger both.
\end{itemize}
\end{battle}

\pickup{Power Wristband}{behind the Ghouls.}

\begin{menu}
\begin{itemize}
    \item \textbf{Equipment}
    \begin{itemize}
        \item Lightning
        \begin{itemize}
            \item Optimize: Offensive (Gladius \& Power Wristband)
        \end{itemize}
    \end{itemize}
\end{itemize}
\end{menu}

Dodge the Ghast by dodging to his left when he swings. A guaranteed alternative is to lure him forward, run to left corner outside door for 2 seconds, then run in front of him.

Check shrouds. Minimum required 2 Deceptisols/Fortisols, safety is 4 Deceptisols/2 Fortisols.

Ghoul hallway is as follows: {\bf Fortisol, Deceptisol, Deceptisol, Fortisol, Deceptisol}

%\begin{enumerate}
%    \item Fortisol
%    \item Deceptisol
%    \item Deceptisol
%    \item Fortisol
%    \item Deceptisol
%\end{enumerate}

\begin{battle}{Ghoul}
\begin{itemize}
    \item Wait 33 ({\bf PW Skip}: 41) seconds before attacking
    \item If Sazh doesn't get hit, once the chain gauge is 106.5\%
\end{itemize}
\end{battle}

\textbf{Fortisol} on the elevator.

\begin{battle}{Anima (With PW)}

\begin{itemize}
    \item Blitz target the Right Manipulator. Execute on Anima after Snow + Sazh attack it
    \item Blitz Anima again after swipe
    \item When the Left Manipulator is dead, hover over the Right Manipulator again, execute on Anima
    \item Auto-battle until the end of the fight.
    \item Potion if anyone is red, especially after the arms respawn.
\end{itemize}
\end{battle}

\begin{battle}{Anima (PW Skip)}

\begin{itemize}
    \item Blitz Anima while dodging his counters until the Left Manipulator dies, using Potions as necessary
    \item Attack until half health
    \item Kill the Right Manipulator
    \item Auto-battle.
\end{itemize}
\end{battle}

\save{2}

\save{3}

\end{multicols}
