\chapter{Ahriman}
\begin{menu}
\party{\vaan}
\end{menu}
\begin{enumerate}
	\item Setup Traveler on the first Zombie Knight, making note of your number.
	\item \pickup{Officer's Hat, 12.5\% chance, selling for 3,500}{Somewhere}
	\item Setup a Hi-Potion warp with \basch. Despawn glitch through the area.
\end{enumerate}
\begin{menu}
\party{\vaan, \balthier, \ashe}
\begin{itemize}\item \leader{\balthier}\end{itemize}
\end{menu}
\begin{equip}
\begin{itemize}
\vaanf Remove Mirror Mail
\end{itemize}
\end{equip}
\begin{liscense}
	\begin{itemize}
		\startLic{ashe}{%
			\item Magick Lore 40
			\item Channeling 30
			\item Warmage
			\item Headsman
			\item Swiftness 30
		}
		\nextLic{penelo}{%
			\item CHannelin 30
			\item Warmage
			\item Swiftness 30 \textit{if you got it on \ashe\ as well}
		}
		\nextLic{vaan}{%
			\item Libra
			\item Belias
			\item Poenix Lore 1
			\item Potion Lore 2
			\item Spellbound
			\item Swiftness 30
		}
	\end{itemize}
\end{liscense}
\begin{enumerate}[resume]
	\decoy{\ashe}{\vaan}
	\item \balthier\ can Protect \vaan\ for safety
	\item \vaan\ Hi-Potion
\end{enumerate}
\begin{menu}
\party{\vaan}
\end{menu}
\begin{enumerate}[resume]
\optimize{\vaan}
\item Run past the last group of enemies
\gambiton{\vaan}
\item Enter the fight
\end{enumerate}
\begin{battle}{Ahriman}
\begin{itemize}
\ifc{\enemy{Ahriman} opens with \textbf{Phantasmal Gaze}}
	{
		\item Wait for the animation to start, then continue
	}
\ifc{\vaan\ gets confused}{\item Remove his Weapon}
\begin{menu}
\begin{itemize}
\girlsin
\item \GirlsGambitOn
\end{itemize}
\end{menu}
\vaanf Run behind \enemy{Ahriman} so that \enemy{Ahriman} is facing away from the girls, so that \textbf{Phantasmal Gaze} doesn't hit them.
\item Let exactly 2 \fira s hit \enemy{Ahriman}, 1 per cast off of a single Reflect, not a full round. Letting 3 reset
\atbresetgirls
\battlewait
\gambitoff{\vaan} once he gets a successful scteal.
\item Let a full round of \fira s hit \enemy{Ahriman}, so that a total of 8-9 have hit.
\beliasfreeze\ so that \enemy{Ahriman} doesn't Teleport.
\item Let another full round of \fira s hit, pay attention to who gets off the \fira\ first.
\beliasfreeze{when both caster's ATB reaches the ``F'' in \fira}
\item After the \fira s are done, then:
\begin{itemize}
\item Whoever got the first \fira\ off (usually \penelo): Hi-Potion \enemy{Ahriman}
\item Whoever got the second \fira\ off (usually \ashe): Warp Mote
\vaanf Steal \enemy{Ahriman}
\end{itemize}
\item \enemy{Ahriman} Teleports
\vaanf Run behind \enemy{Ahriman}, paying attention to which way that he's facing.
\begin{menu}
\begin{itemize}
\girlsout
\gambitoff{Turn the Hi-Potion user's}
\end{itemize}
\end{menu}
\item Close the menu and immediately reopen it
\begin{menu}
\begin{itemize}
\girlsin \gambiton{Turn the Hi-Potion user's}
\end{itemize}
\end{menu}
\item Do another round of \fira s
\beliasfreeze{the same way that you did before.}
\item After the damage lands:
\begin{menu}
\begin{itemize}
	\item ATB Reset everyone by removing their Armor and then Optimizing them all
	\item Config: Battle Speed Slowest \textit{if Swiftness is on both girls else} Battle Speed Second Slowest
\end{itemize}
\end{menu}
\item Let the \fira s charge slowly.
\item As soon as \enemy{Ahriman}\ teleports to you briefly:
\begin{itemize}
\beliasfreeze{should be about when the ATB is charged to the ``r'' in \fira}
\end{itemize}
\item Once \enemy{Ahriman} dies, \GirlsGambitOff
\end{itemize}
\end{battle}
\begin{enumerate}[resume]
\item Config: Battle Mode Active
\item \pickup{Elixir (100\%), Gaia Hat/Elixir (50/50)}{in the room}
\end{enumerate}