\chapter{Firemane}
\begin{enumerate}
	\item Go back to the \textbf{Eastgate}, talk to \textbf{Kytes}, \cs, \cs, \cs
	\item Head straight \east\ to \lowtown
	\item Go \south\ to the \textbf{South Sprawl}
	\item Go \south\ to \textbf{Old Dalan's Place} on the right, near the next exit, \cs
	\item Exit \south\ to the \textbf{Southgate}, then \south\ to \textbf{Giza}. Pickup \textbf{Potion} from the first chest you see.
	\item \cs, go straight south to the Nomad Villiage.
	\item Talk to the Nomad on the right, near the chest. \cs. Exit through the \south\west.
	\item Head \south\ to the next zone, then \east\ to speak to \textbf{Nomad Youth}
	\item Run around collecting sunstone energy
	\item Go \north\ back to \rabanastre
\end{enumerate}

\begin{equip}
	\begin{itemize}
		\vaanf Remove Armor
		\penelof Remove Everything
	\end{itemize}
\end{equip}
\begin{enumerate}
	\item Go to \lowtown, then go to \textbf{Old Dalan's Place}, \cs. Talk to \textbf{Old Dalan}, \cs, leave, \cs
	\item Head \north\ to the \textbf{North Sprawl}, then take the first exit to the \north-\east\ to the \textbf{Streets of Rabanastre}
	\item Go \south\ to \textbf{Migelo's Sundries}
\end{enumerate}
\begin{shop}{1\,250}
	\sell[exception]{1 Armor, 1 Potion, 1 Teleport Stone, All Phoenix Downs}
	\buy{Phoenix Downs up to 8}
\end{shop}
\begin{enumerate}
	\item Go to the \textbf{Southern Plaza} straight in front of you, then go straight \west\ to the \textbf{Westgate}. Go to the \westersand, \cs
	\item Go to the first \north\east\ exit, then hit yourself down to below 10\% HP. Flee when ATB is at 2/3.
\end{enumerate}

\begin{center}
	\begin{tabular}{|c|c|c|} \hline
	Min HP & Max HP & Action \\ \hline
	      19	& 25&	Punch+Armor\\ \hline
	      26	&26	&Wolf/YOLO Punch+No Armor\\ \hline
	      27	&33	&Punch+No Armor\\ \hline
	      34	&38	&Sword+Armor\\ \hline
	      39	&40	&Punch+Armor x2\\ \hline
	      41	&46	&Punch+Armor, Decide\\ \hline
	      47	&51	&Sword+No Armor\\ \hline
	      52	&56&	Punch+No Armor x2\\ \hline
	\end{tabular}
\end{center}
\begin{enumerate}
	\item Set Battle Speed to Slow
\end{enumerate}
\begin{equip}
	\begin{itemize}
		\vaanf Optimize
	\end{itemize}
\end{equip}
\begin{battle}{Dustia}
	\begin{itemize}
		\item Run over the load line
		\item Run back a bit, positioning yourself near the load line.
		\item \textbf{Dustia} spawns
		\item When the HP bar appears, throw a Phoenix Down on Dustia
		\item Try to pick up whatever drops there are, cross the load line before the EXP from Dustia appears on screen.
		\item Do this 8 times total.
	\end{itemize}
\end{battle}
\begin{enumerate}
	\item Run straight \north, then \north\west to the \textbf{East End}, then take the \lowtown\ entrance \north
	\item Head \north\east\ to the Sewer Entrance, near the brats on the crates
	\item Go into the \waterway, \cs. \save
	\item Follow the path, \flee-ing all the while, until you go up the stairs to the palace. \cs, \cs Can get the chest in the first waterway because it can have remedy/ether
	\item Check for the treasure chests, first the two in the \south\east, then one to the \west, then the \north\east, then the \north\west
	\item Try to get past the guard, then talk to the \textbf{Palace Servant}. Run around the guard, go up the stairs through the door.
	\item Describe shouting stuff to lure guards? \south\west, shout. Back to the entrance, call, then loop around tio the lion - go a bit further, call the guards, then show the sigil to the wall.
	\item In the \textbf{Secret Pasageway}, go straight forward, activate the switch, then go through the suspicious wall.
	\item \cs, mash, \cs.
\end{enumerate}
\begin{liscense}
	\begin{itemize}
		\vaanf
		\begin{itemize}
			\upl{Accessories 2}
			\leftl{Black Magic 1}
		\end{itemize}
	\end{itemize}
\end{liscense}
\begin{gambit}
	\begin{itemize}
		\charactergambit[Off]{\vaan}{\gambitline[enemy]{(Foe: Nearest Visible)}{(Phoenix Down)}}{\gambitdelete}
		\charactergambit{\balthier}{\gambitdelete}{\gambitline[enemy]{Foe: Party Leader's Target}{(Steal)}}
		\charactergambit[Off]{\fran}{\gambitdelete}{\gambitline[enemy]{Foe: Party Leader's Target}{(Fire)}}
	\end{itemize}
\end{gambit}
\begin{enumerate}
	\item \leader{\fran}, \save. Make sure that you fight 2 Ggiantoads.
\end{enumerate}
\begin{battle}{Gigantoad}
\begin{itemize}
\vaanf Fire
\franf Fire
\end{itemize}
\end{battle}
\begin{enumerate}
	\item Go down stairs, \cs
\end{enumerate}
\begin{battle}{Guard Fight}
	\begin{itemize}
		\item \leader{\vaan}
		\franf Fire a guard that isn't the default, targeting whoever is futhest from \ashe
		\vaanf Same as \fran
		\item Make sure that Amalia doesn't get any kills
	\end{itemize}
\end{battle}
\begin{enumerate}
	\item \cs
	\item Use \balthier\ first aid to keep him in place, and \fran\ potion \vaan. Use \vaan\ to \pickup{Leather Shield}{around the corner}. \leader{\fran} to trigger the Flan Fight.
\end{enumerate}
\begin{battle}{Flan}
	\begin{itemize}
		\franf Fire a Flan that isn't the default, by targeting the Flans that are close to Amalia but that she isn't targeting.
		\vaanf Same as \fran
	\end{itemize}
\end{battle}
\begin{enumerate}
	\item \cs. \pickup{Phoenix Down/Red Fang}{next screen}
	\item If Amalia stole a kill, then kill 2 Gigantoads. Otherwise, steal from them with \balthier\ if money is bad, have \fran\ keep on running
\end{enumerate}
\begin{gambit}
	\begin{itemize}
		\vaanf \textbf{OFF}
		\franf \textbf{ON}
		\balthierf \textbf{OFF}
	\end{itemize}
\end{gambit}
\begin{battle}{Firemane}
	\begin{itemize}
		\vaanf Attack
		\balthierf Attack
		\item When Firemane uses bushfire, use a potion to stall. He takes 20\% more damage in the water, but he will teleport to use Bushfire, so you can try to lure him away.
		\item Try to lure and keep Firemane in the water. Can steal with \balthier\ if you need money.
		\item Queue up Fire, by putting the cursor on Black Magic, before the next fight
	\end{itemize}
\end{battle}
