\chapter{Hashmal}
\begin{enumerate}
\item Cure \vaan\ to full, when he's still in reserve
\end{enumerate}
\begin{menu}
\party{\vaan, \ashe, \penelo}
\end{menu}
\begin{enumerate}[resume]
\item Cure Reddas to ful while running.
\item At the start of the Third Ascent:
\begin{enumerate}
\penelof Immobilize the Party, such that \ashe, \penelo, Reddas all get Immobilized
\ashef Float Mote Party
\vaanf Run back to the Black Waystone up North
\end{enumerate}
\item Run past the enemies on the next screen. Despawn once you appraoch the second group of enemies by swapping leaders to the Immobilized people briefley.
\item Smack the fake wall on the right and use the Waystone. Be careful of the traps
\penelof Reflect Reddas
\item If a chest spawns here, then it's eitehr an Elixir or 999 Gil.
\item Go through the two fake walls, choose the Red Waystone (at the back right).
\item During this, Aeronite can deal 1500+ Damage, so make sure that \vaan\ doesn't die to it
\item Choose the Pink Waystone, in front of you on the right
\item Run Right
\ashef Reflect \ashe
\penelof Reflect \penelo
\item Smack the fake wall
\girlsout
\item Heal \vaan\ if he's below 1200HP. Instead, you can try to avoid \vaan\ getting hit if you move well.
\item Use the Waystone, and use the lift to start the fight.
\end{enumerate}
\begin{battle}{Hashmal}
\begin{itemize}
	\item Make sure that \vaan\ is targeted.
	\begin{menu}
	\party{\vaan, \ashe, \penelo}
	\end{menu}
	\begin{equip}
	\begin{itemize}
	\ashef Cherry Staff
	\penelof Cherry Staff
	\end{itemize}
	\end{equip}
	
\begin{gambit}
	\begin{itemize}
		\ashegambit{Aeroga}
		\penelogambit{Aeroga}
	\end{itemize}
\end{gambit}
	\vaanf Run around the girls
	\beliasfreeze
	\ifc{Reddas is Full HP and \vaan\ can take a hit, 1200+HP}{\item It's good to let \enemy{Hashmal} get one move off, to make it less likely that Reddas gets countered}
	\ifc{Reddas got hit by the Tower or \vaan\ is low on HP}{\item Try to avoid \vaan\ from getting hit}
	\item After all 8 Aerogas from the first round land:
	\begin{equip}
	\begin{itemize}
		\vaanf Remove Weapon
	\end{itemize}
	\end{equip}
	\item ATB Refresh \penelo, \ashe, by removing their weapons and then equipping Flame Staff and Cherry Staff
	\item Let the Gambits Kill
	\item Right before the fight ends, \GirlsGambitOff
\end{itemize}
\end{battle}