\chapter{Hydro}

\begin{equip}
	\begin{itemize}
		\vaanf Remove Mirror Mail
		\penelof Remove Golden Amulet, Glacial Staff
		\ashef Remove Golden Amulet, Glacial Staff
	\end{itemize}
\end{equip}
\begin{liscense}
	\begin{itemize}
		\startLic{balthier}{\item Nothing}
		      \nextLic{penelo}{\item Black Magick 5 \item Quickening}
		      \nextLic{ashe}{\item Black Magic 5 \item Shemhazai \ifc{If can afford}{\item Headsman \item Swiftness \item Spellbound}}
		      \nextLic{penelo}{\item Channeling 80 \ifc{If you also got them for \ashe}{\item Headsman \item Swiftness \item Spellbound}}
		      \nextLic{vaan}{\item Remedy Lore 3 \item HP+200}
	\end{itemize}
\end{liscense}
\begin{enumerate}
	\item Once you get to Balfonheim
\end{enumerate}
\begin{shop}{123123}
	\begin{itemize}
		\item Magick Shop:
		      \sell[everything]{Armor, Flame Staves, Cherry Staves}
		      \buy{Firaga}
		\item Item Shop:
		      \buy{X-Potions, Phoenix Downs}
		\item Spend all of your money, and get as mnay healing items as you can. Having at least 10 of each X-Potions and Phoenix Downs is recommended. You can also buy some extra Remedies and Gold Needles if you have extra money; Gold Needles you're usually fine without one, but having an extra Remedy can be useful.
	\end{itemize}
\end{shop}
\begin{enumerate}
	\item Once you get to Ridorana:
	\item Run past enemies on the next two screens.
	      \ashef Reflect Reddas
	\item Once \ashe\ catches up:
	      \begin{itemize}
		      \penelof \fira \ashe
		      \ashef Reflect \ashe
	      \end{itemize}
	\item Continue onto the next screen.
	      \penelof Reflect \penelo
	      \decoy{\ashe}{\vaan}
	\item \castprotect{\vaan}{\vaan}
	\item Set your Cursor onto Green Magic, Oil
\end{enumerate}
\begin{menu}
	\party{\vaan, Reddas}
\end{menu}
\begin{equip}
	\begin{itemize}
		\optimize{\vaan, \penelo, \ashe}
	\end{itemize}
\end{equip}
\begin{battle}{Hydro}
	\begin{itemize}
		\vaanf Run Close, then once \vaan gets targeted:
		\girlsin

		\begin{gambit}
			\begin{itemize}
				\ashegambit{Firaga}
				\penelogambit{Firaga}
			\end{itemize}
		\end{gambit}
		\penelof Oil the party
		\item Wait until \enemy{Hydro} doesn't use Countdown, Bile, Fireball, or Darkra.
		      \vaanf Once he aggros onto \vaan, he will start walking towards \vaan. Run around in a circle while keeping the camera focused to run loop de loops, keeping \ashe, \penelo\ between \vaan\ and \enemy{Hydro} and let them kill.
		\item After the last round of Firagas go off, then \GirlsGambitOff Flee.
	\end{itemize}
\end{battle}