\chapter{Judges}
\begin{gambit}
	\begin{itemize}
		\vaanf \textbf{ON}
		\balthierf \textbf{ON}
		\franf \textbf{OFF}
	\end{itemize}
\end{gambit}
\begin{shop}{9750 - 250/Pheonix Down}
	\sell[everything]{Leather Cap, Leather Armor, Lightwove Shirt, 1 Teleport Stone, Keep at least 1 Potion and as many healing items as possible}
	\buy{Up to 39 Phoenix Downs}
\end{shop}
\begin{enumerate}
	\item Blizzard, Fire \vaan\ before Dustia. Optimize \vaan.
	\item Use the table below to determine how to bring \vaan\ into critical HP. The Fire strats will only work if it's sandstorm or cloudy, otherwise it's the same as Blizzard.
\end{enumerate}
\begin{center}
	\begin{tabular}{|c|c|c|} \hline
		Min HP & Max HP & Action            \\ \hline
		31     & 38     & Punch+Armor       \\ \hline
		49     & 57     & Punch+No Armor    \\ \hline
		110    & 128    & Blizzard+Armor    \\ \hline
		132    & 149    & Blizzard+No Armor \\ \hline
		133    & 153    & Fire+Armor        \\ \hline
		158    & 179    & Fire+No Armor     \\ \hline
	\end{tabular}
\end{center}
\begin{enumerate}
	\item Farm Dustia the same way as above, 39 times, until you get to Level 20.
	\item If Dustia heals you, then go back into the Dustia zone, Attack self, then start Fleeing when the ATB is at the first ``T'' in Attack.
	\item Potion and run up. If it's sunny you can kill a wolf with Fire, if you need some extra LP. Turn off \vaan\ gambit after Dustia
	\item Lots of movement here. (Don't talk to Tomaj - he has 300 gil, 2 potions, 1 teleport stone). Need about 14k gil overall - 14k for things, 5k for Flame Staves if you don't have them dropped. That tells you how much you have extra.
\end{enumerate}
\begin{shop}{1000}
	\sell{Books of Origins, All but 2 Flame Staves}
	\buy{4+ Phoenix Downs}
\end{shop}
\begin{enumerate}
	\item Killer Bow Chest, in the mines. 15\% chance to get it, worth 1k gil. There's also a Assassin's Dagger chest, 12\% to get, for 700 gil.
	\item Try to get the max number of people per testify - can tell by who turned. Book guy and girl, in the shop get all 4 on the carpet.
	\item Party - \vaan, \balthier, \basch
\end{enumerate}
\begin{liscense}
	\begin{itemize}
		\startLic{vaan}{%
			\leftl{Green Magic 1}
		}
		\nextLic{basch}{%
			\downleftl{Daggers 1}
			\leftl{Guns 1}
			\upl{Poles 1}
		}
		\nextLic{balthier}{%
		\item Poles 1
		      }
		      \nextLic{basch}{%
			      \downl{Rods 1}
			      \downl{Staves 2}
		      }
	\end{itemize}
\end{liscense}
\begin{equip}
	\begin{itemize}
		\item Optimize \basch, \vaan
	\end{itemize}
\end{equip}
\begin{enumerate}
	\item Fire, Fire, Attack in the first room, then Fire Attack Vossler to put him into Critical.
\end{enumerate}
\begin{battle}{Judges}
	\begin{itemize}
		\item Flee into the corner to bunch everyone up
		      \vaanf Attack Judge A
		      \baschf Attack Judge B
		      \balthierf If Vossler is below 100 HP, Potion
		\item Phoenix Down anyone but \balthier
	\end{itemize}
\end{battle}
\begin{shop}{3\,900}
	\buy{Cherry Staff, Topkapi Hat, Kilimweave Shirt, Dark, Protect, Reflect, Immobilize}
\end{shop}
\begin{enumerate}
	\item Cure with \balthier if \basch\ is below 400 HP, or if \vaan\ is below 300 HP or is poisoned.
	\item If short on gil, can pickup chests. Party \vaan, \penelo, \ashe
\end{enumerate}
\begin{liscense}
	\begin{itemize}
		\startLic{basch}{%
		\item Nothing
		      }
		      \nextLic{ashe}{%
		\item $\rightarrow\uparrow$: SmallSwords 1
		      \leftl{Staves 1}
		      }
		      \nextLic{penelo}{
		\item Staves 1
		      }
		      \nextLic{vaan}{%
		\item $\uparrow\rightarrow$: Light Armor 2
		      }
		      \nextLic{penelo}{%
		\item Light Armor 2
		      \upl{Mystic Armor 1}
		      \rightl{Mystic Armor 2}
		\item $\nearrow$ on other board: Black Magic 1
		      }
		      \nextLic{ashe}{%
		\item $\rightarrow\uparrow$: Accessories 4
		      \leftl{Black Magic 2}
		      }
		      \nextLic{penelo}{%
		\item Black Magic 2
		      \leftl{Time Magic 1}
		      }
		      \nextLic{vaan}{%
		\item Time Magic 1
		      \upl{Time Magic 2}
		      }
		      \nextLic{penelo}{%
		\item Time Magic 2
		\item $\downarrow\leftarrow$: Arcane Magic 1
		      }
		      \nextLic{vaan}{%
		\item Arcane Magic 1
		      }
		      \nextLic{ashe}{%
		\item $\downarrow\downarrow$: White Magic 3
		      \downl{Gambit Slot 20}
		      }
		      \nextLic{penelo}{%
		\item $\rightarrow\rightarrow$: Gambit Slot 15
		      \downl{Potion Lore 1}
		      \leftl{Gambit Slot 30}
		      \leftl{Magic Lore 25}
		      }
		      \nextLic{ashe}{%
		\item Magic Lore 25
		      }
		      \nextLic{penelo}{%
			      \leftl{Spellbreaker}
		      }
	\end{itemize}
\end{liscense}
\begin{equip}
	\begin{itemize}
		\item Optimize \ashe, \penelo
	\end{itemize}
\end{equip}
\begin{battle}{Judge Ghis}
	\begin{itemize}
		\penelof Dark \penelo
		\vaanf Reflect \ashe
		\ashef Heal \vaan
		\penelof Reflect \penelo
		\vaanf Reflect \vaan
		\item Battle:
		      \vaanf Dark Guard B
		      \penelof Dark Guard B
		\item \leader{\penelo}
		      \ashef Attack \penelo\ only if \penelo\ does not get Tri-Attacked, and isn't in Red HP, to bring her to critical
		      \vaanf Dark \penelo
		      \penelof Dark \penelo
	\end{itemize}
\end{battle}