\chapter{Mandragoras}
\begin{menu}
	Party: \basch, \balthier, \fran
\end{menu}
\begin{enumerate}
	\item Get as many Cures onto \basch\ as possible. Someone protect \basch, and can also Protect \fran\ and \balthier
	\item Teleport to Mt. Bur-Omisace
	\item Before the Bergan Door: \travelerensure{50}
\end{enumerate}
\begin{menu}
	Party: \vaan
\end{menu}
\begin{equip}
	\begin{itemize}
		\item Optimize: \vaan
		      \vaanf Equip Golden Amulet if it's not already on him
	\end{itemize}
\end{equip}
\begin{battle}{Bergan}
	\begin{itemize}
		\vaanf Run up to Bergan
		\item Bring in \ashe, \penelo
		      \begin{liscense}
			      \startLic{ashe}{%
				      \item Mystic Armor 6
			      }
			      \nextLic{penelo}{%
				      \item Mystic Armor 6
			      }
			      \nextLic{vaan}{%
				      \item Shields 4
				      \item Heavy Armor 6
				      \item \textit{Whatever you didn't get before and can afford from:}
				      \begin{itemize}
					      \item Libra
					      \item Belias
					      \item Phoenix Lore 1
					      \item Potion Lore 2
					      \item Spellbound
				      \end{itemize}
			      }
			      \nextLic{ashe}{%
				      \item Ether Lore 1
				      \item Magick Lore 40
				      \item Channeling 30
				      \item Headsman
				      \item Spellbound
			      }
			      \nextLic{penelo}{%
				      \item Channeling 30
				      \item Warmage
				      \item Swiftness
				      \item Spellbound \textit{only if you got it for \ashe as well}
			      }
		      \end{liscense}
		      \vaanf Steal for a $9.7\%$ chance of a Ruby Ring
		      \vaanf Traveler on the correct number.
		      \vaanf Can put Belias in the queu once the second round of Firas go off, to make the enemies stop attacking.
		\item At the end of the fight, \AllGambitsOff
		\item \enemy{Bergan} can block Magicks. If he blocks too many of them, you don't kill. Try your best to recover, and make sure that \ashe\ is alive at the end of the fight.
	\end{itemize}
\end{battle}
\begin{shop}{1232}
	\buy{2 Sorc Armor; Equip, \textit{Optional} 2 Glacial Staves}
\end{shop}
\begin{battle}{Pumpkin Heads}
	\begin{itemize}
		\vaanf Traveler
		\ashef Blizarra
		\begin{menu}
			\begin{itemize}
				\item \travelercheck
				      \penelof Remove Weapon
			\end{itemize}
		\end{menu}
	\end{itemize}
\end{battle}
\begin{enumerate}
	\item Use a cure warp with \penelo\ before talking to the Moogle to freeze her by the entrance to the screen.
	      \ashef Cure herself to make her fall behind
	      \penelof Fira \ashe\, keep running with \vaan\ so that he doesn't get hit, so that they end up in critical. Reflect them both, then pull them out of the party and give \penelo\ a Flame Stave.
\end{enumerate}
\begin{shop}{12200}
	\buy{Mirror Mail; Equip, Bio, Dispel, 3 Remedies, 10 Hi-Potions}
	You need 5400 Gil after the shop. If you can get to above 12200 Gil afterwards, it's worth also:
	\sell{Shielded Armor, Other Unequiped Armor, Megalixir, Ruby Ring, Keep 2 Teleport Stones}
\end{shop}
\begin{battle}{Mandragora}
	\begin{itemize}
		\vaanf Wait for them to gather up, then Traveler them.
		\item Use Reflected Firas until they all die.
	\end{itemize}
\end{battle}