\chapter{Mateus}
\begin{menu}
Party: \vaan, \ashe, \penelo
\end{menu}
\begin{equip}
	\begin{itemize}
		\vaanf Remove Mythril Blade, Escutcheon
		\item Optimize \ashe, \penelo
		\baschf Remove All
		\balthierf Remove All
	\end{itemize}
\end{equip}
\begin{shop}{3\,000}
	\sell[everything]{Cherry Staff, Flame Staves, Equipped Armor, Teleport Stones}
	\buy{Fira, Golden Amulet (if can afford), 10-15 Phoenix Down; Max of 1 less than you can afford, Smelling Salts x Max}
\end{shop}
\begin{gambit}
	\begin{itemize}
		      \charactergambit{\vaan}{\gambitline{(Ally: Any)}{(Smelling Salt)}}{\gambitline[enemy]{(Foe: Nearest Visible)}{(Steal)}}
		      \charactergambit{\penelo}{\gambitline{Ally: \penelo}{Reflect (OFF)}}{\gambitline[enemy]{Enemy: Nearest Visible}{(Fira)}}
		      \charactergambit{\ashe}{\gambitline{Ally: \ashe}{(Aero) (OFF)}}{\gambitline[enemy]{Enemy: Nearest Visible}{(Fira)}}
	\end{itemize}
\end{gambit}
\begin{battle}{Jellies}
	\begin{itemize}
		\item 3-4 rooms for Jellies 1, until you have 34 liquids. Reduce this number by 9 per Golden Amulet. To respawn go out of 2 areas. Can toggle \ashe\ gambit on and off to have it target different Jellies. Each room has about 15-20 Jellies. Need 2 Teleport Stones.
		\item If you have Golden Amulet, License and equip on \vaan\ as soon as he has LP for it, usually by the end of the second room.
	\end{itemize}
\end{battle}
\begin{liscense}
	Once 95 LP on Penelo, do the license menu
	\begin{itemize}
		\startLic{penelo}{%
			\rightl {Intercession/Quickening}
			\rightl{Accessories 8}
		}
		\nextLic{ashe}{%
			\item{Accessories 7}
			\upl{Accessories 8}
		}
		\nextLic{vaan}{%
			\item $\downarrow\downarrow$: Accessories 4
			\upl{Accessories 7}
			\upl{Accessories 8}
		}
	\end{itemize}
\end{liscense}
\begin{shop}{123312}
	\sell{Water Magicites, Yellow Liquids}
	\buy{Golden Amulet up to 3; Equip on to \ashe\ + \vaan\ + \penelo, Warp, Confuse, Decoy, Blizzara, 15 Hi-Potions, 10 Phoenix Down}
\end{shop}
\begin{enumerate}
	\item Need 50k Gil after Jellies 2, and 152 LP on \penelo. Can use calculator to determine how many jellies you need, usually about 6~ the second time. Need 5 Teleport Stones afterwards, 1 Float Motes. There are uses for 4 bonus Float Motes.
	\item After jellies, set cursor for \ashe\ to Blizzara, \penelo\ to Immobilize. Turn off \vaan, \ashe, \penelo\ Gambits.
	\item \textit{If you have at least 4 Float Motes:} Float Mote on \vaan\ to go over the traps.
\end{enumerate}
\begin{shop}{7\,500}
	\sell{Water Magicite, Yellow Liquid}
	\buy{Red Cap \textit{if you didn't buy it before}; Equip, 2x Mage's Hat; Equip, Briandine or Shielded Armor; whichever you didn't buy before}
	Should have about 40k Gil remaining
\end{shop}
\begin{menu}
Party: \vaan, \basch
\end{menu}
\begin{liscense}
You need about 160LP on \ashe\ and 190LP on \penelo\ in order to do the full menu.
\begin{itemize}
	\startLic{ashe}{%
		\leftll{Time Magick 2}
		\leftl{Time Magick 3}
		\leftl{Arcane Magick 3, \textit{if you had 160+LP}}
	}
	\nextLic{balthier}{%
		\item $\rightarrow\downarrow\downarrow$: Green Magick 1
		\leftl{Green Magick 2}
		\leftl{Green Magick 3}
	}
	\nextLic{penelo}{%
		\downll{Ether Lore 1}
		\leftl{Magick Lore 40}
		\upl{White Magick 5}
		\item Green Magick 4, \textit{if you had 190+LP}
	}
	\nextLic{vaan}{%
		\item \textit{If you have 190-224 LP:} Libra, Belias
		\item First Aid
		\item $\downarrow\downarrow\leftarrow\leftarrow$: Poach
		\downl{Traveler}
		\leftl{Shield Block}
		\item Remedy Lore 1
		\ifc{As many of these as you can:}{%
			\item Phoenix Lore 1
			\item Potion Lore 2
			\item Spellbound
		}
	}
	\nextLic{ashe}{%
		\item Mystic Armor 2, on bottom left board
		\upl{Mystic Armor 3}
	}
	\nextLic{penelo}{%
		\item Mystic Armor 3
		\rightl{Mystic Armor 5}
	}
	\nextLic{ashe}{%
		\item Mystic Armor 5
	}
\end{itemize}
\end{liscense}
\begin{equip}
\begin{itemize}
\item Optimize \vaan, \penelo, \ashe, \basch
\baschf Dawn Shard
\end{itemize}
\end{equip}
\begin{enumerate}[resume]
	\item Dismount Chocobo before opening door, \leader{\basch}
	\item Turn off \basch\ Gambits
	\item Use Pedestal, with Dawn Shard on your leader
	\vaanf Traver on Guardian. \basch\ \pickup{Megalixir/Elixer}{nearby}. \travelercheck S et Battle Speed to slowest.
	\item In the next room: \vaan\ Potion \vaan, \basch\ Run Away, \vaan\ Potion \basch\ (should never go off). Run a little wide so that \vaan\ stays still, \basch\ touch the Pedestal (With the Dawn Shard equipped). \leader{\vaan}, leave room.
	\item Can heal in the room with the Fake Crystal
	\item In the room after: \basch\ use Phoenix Down x2, Flee once he starts to use the second one. \vaan\ touch the sword, \leader{\basch}
	\item Run past the Bats and the Guardian in the following rooms.
\end{enumerate}
\begin{menu}
\begin{itemize}
\item Party: \vaan, \ashe, \penelo
\battlefast
\end{itemize}
\end{menu}
\begin{gambit}
\begin{itemize}

\vaanf \textbf{OFF}
\ashegambit{Fira}
\penelogambit{Fira}
\item Set all the gambits to OFF %Tyton fix this later
\end{itemize}
\end{gambit}
\begin{enumerate}[resume]
	\ashef Blizzara \penelo
	\penelof Immobilize \ashe
	\item Cursor	Prep Reflect (Vaan)
	\item Can swap leaders to the immobilized characters to despawn enemies.
\end{enumerate}
\begin{battle}{Vinsukur}
	\begin{itemize}
		\vaanf Reflect \ashe, \penelo\ at the stairs.
		\item \GirlsGambitOn
		\vaanf Flee to the corner and stay.
		\item At the end of the fight, \GirlsGambitOff
		\item If Vinuskar pushes the girls, move them away from \vaan.
	\end{itemize}
\end{battle}
\begin{enumerate}[resume]
	\ifc{\ashe\ doesn't have Arcane Magick 3}{%
	 \item Liscense it immediately
	 \penelof Liscense Green Magick 4
	}
	\penelof Action on \vaan (Potion or cure, shouldn't ever go off).
	      \ashef Decoy \vaan
	      \vaanf Touch the statue, then Reflect \vaan
\item \leader{\penelo}, Flee. Once \vaan\ is untargeted:
\end{enumerate}
\begin{menu}
\begin{itemize}
\item Party: \basch, \balthier
\battleslow
\item If \penelo\ doesn't have Green Magick 4, then license it now.
\end{itemize}
\end{menu}
\begin{enumerate}[resume]
	\balthierf Protect \basch
\end{enumerate}
\begin{battle}{Mateus}
	\begin{itemize}
		\item Flee up to Mateus, set the cursor to Green Magic
		\item Party: \vaan, \ashe, \penelo
		\item Equip Dawn Shard onto \vaan
		      \penelof Oil \penelo
		      \item \GirlsGambitOn
		      \vaanf Hi-Potion \vaan, turn on Gambits
		      \item Right before Mateus dies, equip Golden Amulet onto \vaan
		      \item If \ashe\ and \penelo\ have enough MP for another cast, turn off their Gambits
	\end{itemize}
\end{battle}