\chapter{Mimic Queen}


\begin{battle}{Arena}
	\begin{itemize}
		\vaanf Mash Fire
		\balthierf Attack Daguza
		\vaanf Fire Galeedo
		\balthierf Steal Daguza, if 2 Attacks landed
		\vaanf Fire Daguza
		\balthierf Steal Daguza, if 2 attacks landed and no successful steal yet.
	\end{itemize}
\end{battle}
\begin{enumerate}
	\item If you didn't get the elixer chest, there will be an extra.\ chest to pick up with the Tournamline Ring.
	\item Have \balthier\ use First Aid while you pick up 3 gil chests on the side path, then \leader{\balthier}.
	\item Do another first aid warp in the clock tower, after the three chests. \balthier\ use First Aid, \leader{\fran} and start running towards the shop, then have \balthier\ use another First Aid. Once that goes to action, tell \balthier\ to First Aid \fran, which should never go off.
\end{enumerate}
\begin{shop}{400}
	\buy{Light Woven Shirt, Blizzard}
\end{shop}
\begin{enumerate}
	\item \fran\ run to the other switch, then \leader{\balthier}.
	\item Use \balthier to activate the switch, then \leader{\fran}.
	\item Use \fran\ to activate the other switch, then \leader{\balthier}. Leave the zone.
\end{enumerate}
\begin{battle}{Zombie}
	\begin{enumerate}
		\franf Attack x2
		\vaanf Attack x2
	\end{enumerate}
\end{battle}
\begin{enumerate}
	\item \pickup{Phoenix Down}{first room} First mimic in first room, first mimic in second room, then steal from the ones you run past.
\end{enumerate}
\begin{battle}{Mimic}
	\begin{itemize}
		\franf Attack, then Blizzard
		\vaanf Attack, then Blizzard
		\franf Start running away, let everyone else kill.
	\end{itemize}
\end{battle}
\begin{battle}{Flans}
	\begin{itemize}
		\franf Fire
		\vaanf Fire
	\end{itemize}
\end{battle}
\begin{enumerate}
	\item \pickup{Phoenix Down}{third room}. Do the License, then use the new mimic fight for all the upcoming mimics.
\end{enumerate}
\begin{liscense}
	\begin{itemize}
		\balthierf Accessories 1, Black Magic 1
	\end{itemize}
\end{liscense}
\begin{battle}{Mimic}
	\begin{itemize}
		\franf Blizzard
		\balthierf Blizzard
		\vaanf Blizzard
	\end{itemize}
\end{battle}
\begin{enumerate}
	\item \pickup{Buckler}{fourth room} Tell \balthier\ to cure \vaan\ after killing the Flan to freeze him in place. Use \vaan\ to flick the switch, then \leader{\balthier} to exit the room. Keep running.
	\item \pickup{Leatherhelm Chest}{right} Kill 3 mimics back in the third room. Can \pickup{hi-potion}{before the load zone} \save, \leader{\vaan}.
\end{enumerate}
\begin{battle}{Mimic Queen}
	\begin{itemize}
		\item Turn the camera, run backwards to the gate. Blizzard the Mimic Queen with everyone.
		\item At the last round:
		      \begin{equip}
			      \begin{itemize}
				      \item Everyone: Remove All
			      \end{itemize}
		      \end{equip}
	\end{itemize}
\end{battle}