\chapter{Pandemonium}
\begin{enumerate}
	\item Go south at the Central Room. Kill at least 1 \enemy{Chimera Brain} by utilizing a Firaga from both \ashe, \penelo\ and a Reddas attack. Pick up a Black Orb from the first one that you kill.
	      \vaanf Remove Mirror Mail
	\item At the First Pedestal:
	      \begin{itemize}
		      \ashef cure \vaan\ or Reddas
		      \item Place the Orb
		      \item \leader{\ashe} and leave
	      \end{itemize}
	\item On the way back, kill another \enemy{Chimera Brain} for another Black Orb.
	\item When you get back to the Central Room:
	      \begin{itemize}
		      \item Do the Too Far Away trick with either \ashe, \penelo, while you go and place the Orb on the Pedestal.
		      \item Switch the leader to whoever was frozen and leave north.
	      \end{itemize}
	\item Kill the first Chimera on the way back, pick up another Black Orb.
	\item Setup your cursor on Dispel, Confuse, Immobilize, and Green Magicks
	\item At the Last Pedestal:
	      \begin{itemize}
		      \vaanf Protect \vaan
		      \item Setup Cursor on Time Magicks
		      \item Place Orb
		            \begin{equip}
			            \begin{itemize}
				            \optimize{\vaan}
				            \penelof Cherry Staff
				            \ashef Cherry Staff
			            \end{itemize}
		            \end{equip}
		            \begin{gambit}
			            \begin{itemize}
				            \charactergambit[Off]{\ashe}{\gambitline{Ally: \ \ashe\ \ }{Reflect}}{\gambitline{Ally: \ \ashe\ \ }{(Aerora)}}
			            \end{itemize}
		            \end{gambit}
		      \item \leader{\vaan}, leave the room
	      \end{itemize}
	      \penelof Immobilize the Party. Don't start running away too early, everyone but \vaan\ needs to get hit by it.
	      \ashef Reflect \ashe
	\item Run past the enemies and open the door
	      \penelof Reflect \penelo
	      \ashef Reflect Reddas
	      \gambiton{\ashe}
	\item Prep Cursor on White Magicks and heal \vaan\ to full HP
\end{enumerate}
\begin{battle}{Pandemonium}
	\begin{itemize}
		\penelof Dispell
		\vaanf Run a little bit to the right, so that the others don't get hit by Flatten/Power Spin, and so that Reddas can't reach \enemy{Pandemonium}
		\vaanf Confuse once Dispel has charged a bit
		\vaanf Confuse 3 times total
		\penelof Aeroga the Party after inputting the third Confuse
		\item \GirlsGambitOff
		\item If not yet dead, input more Aerogas until death.
	\end{itemize}
\end{battle}