\chapter{Tiamat}

\begin{enumerate}
	\item Go to the clan hall, talk to Montblanc to get a lot of items.
	\item Buy Traveler, make sure that you have 500 gil left for the Chocobo. If you don't have enough gil, then check the next shop to see what is safe to sell.
	\item Ride a Chocobo to Jahara
	\item Get the Jaya Stick, continue
	\item Get on the chocobo, \pickup{Red Cap, Golden Amulet}{2 chests in the Ozmone Plains}
	\item Party: \vaan, \basch, \penelo
\end{enumerate}
\begin{liscense}
\begin{itemize}
	\baschf
	\begin{itemize}
		\item Nothing
	\end{itemize}
	\ashef \rightb
	\begin{itemize}
		\item Rods 1
	\end{itemize}
	\penelof \rightb
	\begin{itemize}
		\item Rods 1
		\downl{Staves 2}
	\end{itemize}
	\ashef \leftb
	\begin{itemize} 
		\item Staves 2
	\end{itemize}
	\vaanf ($\rightarrow\rightarrow$)
		\begin{itemize}
		\item $\nearrow\nearrow$: Shields 1
		\rightl{Light Armor 3}
		\rightl{Heavy Armor 3}
		\rightl{Heavy Armor 4}
		\item $\uparrow\leftarrow$: Light Armor 5
	\end{itemize}
	\baschf ($\rightarrow\rightarrow\rightarrow$)
	\begin{itemize}
		\downl{Heavy Armor 3}
		\upl{Light Armor 5}
	\end{itemize}
	\penelof ($\rightarrow\rightarrow$)
		\begin{itemize}
		\uprightl Headsman on other board
		\end{itemize}
	\balthierf ($\rightarrow\rightarrow$)
	\begin{itemize}
		\item $\rightarrow x4$: Poach
		\downl{Traveler}
	\end{itemize}
	\penelof ($\leftarrow\leftarrow$)
	\begin{itemize}
		\item $\uparrow x7 \leftarrow$: Black Magics 3
	\end{itemize}
	\ashef \leftb
	\begin{itemize}
		\item Black Magics 3
	\end{itemize}
\end{itemize}
\end{liscense}
\begin{enumerate}
	\item Use \penelo\ to try and Berserk \basch, then get back on the chocobo.
	\item Dismount the Chocobo before the cutscene at the barrier. Swap \basch\ with \balthier\ if Berserk landed.
	\item Complete Eruyt, then Teleport to Jahara
\end{enumerate}
\begin{shop}{2\,500}
	\sell{Longsword, Bowgun, Killer Bow, Assassin's Dagger, Escutcheon, Bangle, Tourmaline Ring, Electrum, Arcana x2}
	\buy{Shielded Armor (or Brigandine if your money is super low), Flame Staves up to 2, Gold Needle up to 1, Phoenix Downs up to 4, Red Cap \textit{if you have 23k Gil}, Elixers Healing Items and Mythril Blade if needed}
Need to have 30 gil left over.

Always keep: Tleeport Stone, Warp Mote, Flame and Cherry Staves, Cypress Poles, Mystic Armors
\end{shop}
\begin{enumerate}
	\item Get on Chocobo. When you get off, check for chest, and try to Berserk \basch\ with \penelo\ and then \vaan, then get back on the Chocobo. If you land it, take him out of the party for \balthier.
	\item Get on chocobo again, can repeat the berserk before the loading zone.
	     \item \textit{If you have Brigandine:}
	     \begin{enumerate}
	     	\vaanf Protect \vaan\ while running, make sure it's up for Tiamate. Larsa has healing gambits, so can stop \flee\ if anyone is below 50\%
		\end{enumerate}
	\item Cast Traveler, open the Menu to check Step Count and make note of it. Turn Battle Speed to Min.
	\item Battle Speed to Max. Berserk \balthier
\end{enumerate}
\begin{battle}{Tiamat}
	\begin{itemize}
		\item Change Party: \vaan, \balthier, \basch, Larsa (if he doesn't open with Disablega)
		\vaanf Phoenix Down Tiamat to draw aggro
		\vaanf Dark x2, Equip Magicite
		\vaanf Phoenix Down Tiamat
	      \balthierf Check your step counter to make sure that the last 3 digits don't go above whatever you had before, should be within 1-10 of the previous value. Use Traveler when he flashes Red
	\end{itemize}
\end{battle}
