\chapter{Tyrant}
\begin{enumerate}
\penelof Dispell and Immobilize on \penelo
\item Immobilize despawn all enemies as before
\item At the second intersection, have \ashe\ Cure \vaan\ twice to keep her standing still until \enemy{Diakon Entite} is close
\ifc{Diakon Entite is already close}{%
\item \leader{\ashe}
\balthierf First Aid \balthier\ and First Aid \ashe\ to stand still
}
\item Have the moving character touch the switch, then switch the leader back to the standing still character and leave.
\item At the start of the second zone, \penelo\ Immobilize \penelo. Don't start moving until that has been input.
\item At the second gate, \balthier\ First Aid \balthier\ and First Aid \ashe\ to stand still
\ashef Keep moving forwards, touch the switch, then \leader{\ashe} to leave.
\end{enumerate}
\begin{menu}
\party{\vaan, \ashe, \penelo}
\begin{itemize}
\item Can remove the Mirror Mail if you want.
\end{itemize}
\end{menu}
\begin{liscense}
\begin{itemize}
	\startLic{balthier}{\item Nothing}
	\nextLic{vaan}{%
		\item Arcane Magick 2
	}
	\nextLic{penelo}{\item Channeling 50}
	\nextLic{ashe}{\item Channeling 50 \item Magick Lore 55}
	\nextLic{penelo}{\item Magick Lore 55 \item Gambit Slot 50}
	\nextLic{ashe}{\item Gambit Slot 50 \item Swiftness 50}
	\nextLic{penelo}{\item Swiftness 50}
	\nextLic{vaan}{\item HP+150 \item Potion Lore 3 \item Swiftness 50}
	\nextLic{ashe}{\item Headsman \item Swiftness 30 \item Spellbound}
	\nextLic{penelo}{\ifc{you got them for \ashe}{\item Headsman \item Swiftness 30 \item Spellbound}}
\end{itemize}
\end{liscense}
\begin{gambit}
	\begin{itemize}
		\ashegambit{Blizzara}
		\penelogambit{Blizzara}
	\end{itemize}
\end{gambit}
\begin{enumerate}[resume]
\item Run past the final enemies.
\item Optionally, you can Protect and Decoy \vaan and Optimize him. Without these, he has about a 25\% chance to die at the start of the next battle
\item Reflect both \ashe, \penelo. Do this at the start of the first screen after the enemies if you have Spellbound, just before the fight otherwise.
\end{enumerate}
\begin{battle}{Tyrant}
	\begin{itemize}
		\penelof Dispel
		\vaanf Once it's charged a bit, start spamming Confuse
		\item After the first Confuse, \GirlsGambitOn
		\item Try to keep the girls a bit away, and keep him confuse looped.
		\item At the end of the fight, \GirlsGambitOff
	\end{itemize}
\end{battle}