\chapter{Vossler}

\begin{enumerate}
	\item Gambit \ashe\ On. Can use it to heal if anyone is below 70\% and there aren't enemies nearby by stopping to \flee. \vaan\ can keep Protecting \penelo\ so that she takes less damage. Can also use Reflect to make \penelo\ safter against Sleep.
	\item \vaan\ Reflect \vaan once enemies stop targeting you around the bridges. Gamibit \ashe\ Off. Reflect on the Bridge before the next fight, \leader{\penelo}. Before the zone line, Reflect Vossler, prepare Dark. Take the Forced Save.
\end{enumerate}
\begin{battle}{Garuda}
	\begin{itemize}
		\penelof Dark \ashe, ensure that it lands
		\ashef Attack \penelo
		\penelof If not in critical, then Attack \penelo
		\item Enter the fight
		\item Flee past the first pillar on the left
		\penelof Dark Ashe
		\vaanf Dark Ashe
		\ashef Attack Ashe
		\item Prep cursor on Green Magick
	\end{itemize}
\end{battle}
\begin{enumerate}
\item \vaan\ Protect \vaan\ to freeze, use \penelo\ to run to the shop. \ashe\ Attack \ashe\ if she blocked earlier. If she was hit but didn't get into critical HP, then remove her weapon and then attack.
\end{enumerate}
\begin{shop}{8\,300}
	\buy{Cherry Staff; equip on \penelo, 2 CypressPoles, Sleep, Oil, Berserk, Aero}
\end{shop}
\begin{enumerate}
	\item Remove \ashe, \penelo\ from the party to warp
\end{enumerate}
\begin{liscense}
	\ashe\ Spellbreaker
\end{liscense}
\begin{gambit}
	\begin{itemize}
		\charactergambit[Off]{\vaan}{\gambitdelete}{\gambitline[enemy]{Foe: Nearest Visible}{(Steal)}}
		\charactergambit{\penelo}{\gambitline{(Ally: \penelo)}{(Reflect)}}{\gambitline{(Ally: \penelo)}{(Aero)}}
		\charactergambit{\ashe}{\gambitline{(Ally: \ashe)}{(Aero)}}{\gambitline[enemy]{Enemy: Nearest Visible}{Attack}}
	\end{itemize}
\end{gambit}
\begin{battle}{Demon Wall}
	\begin{itemize}
		\item Make sure that \vaan\ is targeted, then bring in \ashe, \penelo
		\item If Vossler is targeted, then don't bring in the girls. Close the menu and Flee until Annul hits Vossler, then run back, ensure that \vaan\ gets targeted, and continue
		\item If Demon Wall starts with Doom, then immediately take the girls out of the party (turning off Gambits and ATB Reset). Flee until Doom hits \vaan, then run back, ensure that \vaan\ gets targeted, and continue
		      \vaanf Run back out of range
		      \vaanf Protect, Reflect \vaan
		\item At the end of Demon Wall 1, the third round of Aeros, turn off the girl's gambits and Flee.
		\item At the end of Demon Wall 2, once Vossler's reflect wears off, have \vaan Reflect Vossler. Turn on \vaan's gambit. Once the last Aeroes are fired, turn off all gambits and \leader{\ashe}
	\end{itemize}
\end{battle}
\begin{enumerate}
	\item Heal Vossler if near critical. \pickup{elixer}{area}. Make sure \penelo\ has 48 mp
\end{enumerate}
\begin{battle}{Belias}
	\begin{itemize}
		\vaanf Reflect Vossler, then pick up chest
		\vaanf Reflect \vaan
		\item 2 rounds, ATB Refresh at the end of the second round
		      \begin{equip}
			      \begin{itemize}
				      \item Remove All \vaan, \penelo, \ashe, \basch
				      \item Optimize \basch, \balthier, \vaan, \ashe, \penelo
			      \end{itemize}
		      \end{equip}
	\end{itemize}
\end{battle}
\begin{enumerate}
	\item Setup cursor to Reflect, \penelo\ Gambit On
\end{enumerate}
\begin{battle}{Vossler}
	\begin{itemize}
		\ashef Aero Guard
		\vaanf Reflect \vaan
		\penelof Reflect Ashe
		\ashef Gambit On
	\end{itemize}
\end{battle}