\chapter{Chapter 2}

	\begin{battle}[0:10]{Pantheron}
		\begin{itemize}
			\item Attack x2
			\item Repeat
		\end{itemize}
	\end{battle}

	\begin{menu}
		\begin{itemize}
			\item \textbf{Settings}
			      \begin{itemize}
				      \item Battle Speed: Slow
			      \end{itemize}
		\end{itemize}
	\end{menu}

	Farm both 100\% Deceptisols by waiting 23 seconds.
	\begin{battle}[0:23]{Zwerg Scandroid x3 (1)}
		\itemdrop{100}{Deceptisol}
	\end{battle}

	\begin{battle}[0:23]{Zwerg Scandroid x3 (2)}
		\itemdrop{100}{Deceptisol}
	\end{battle}

	\begin{menu}
		\begin{itemize}
			\item \textbf{Settings}
			      \begin{itemize}
				      \item Battle Speed: Normal
			      \end{itemize}
		\end{itemize}
	\end{menu}

	\begin{battle}[0:16]{Pantheron x2}
		\begin{itemize}
			\item Hand Grenade x3, Attack x2 if not dead
			\item Each time, Target Pantheron A while ATB is charging, then switch to Pantheron B for Grenade
		\end{itemize}
		\itemdrop{12}{Fortisol}
	\end{battle}

	Camera trick the dogs after prompt.

	\begin{battle}[0:32]{Zwerg Scandroid x4 (Lightning Lead)}
		\begin{itemize}
			\item Attack after 32 seconds have passed. Should be when Sazh attacks the last one remaining, also go by audio cue.
		\end{itemize}
		\itemdrop{96}{Deceptisol} if got the 0 stars
	\end{battle}

	\pickup{Phoenix Down}{after the scandroids}

	\begin{battle}[0:14]{Pantheron \& Zwerg Scandroid x2 (Lighting Lead)}
		\itemdrop{12}{Fortisol}
	\end{battle}

	\pickup{Gladius}{after the Pantheron}

	\begin{battle}[0:14]{Pantheron \& Zwerg Scandroid x2 (Snow Lead)}
		\itemdrop{12}{Deceptisol}
	\end{battle}
	Access the menu in mid-air.

	\begin{menu}
		\begin{itemize}
			\item \textbf{Settings}
			      \begin{itemize}
				      \item Battle Speed: Slow
			      \end{itemize}
		\end{itemize}
	\end{menu}
	
	\begin{battle}[0:23]{Zwerg Scandroid x3 (3)}
		\itemdrop{100}{Deceptisol}
	\end{battle}

	\begin{battle}[0:32]{Zwerg Scandroid x4 (Vanille Lead) \textbf{Don't Pre-Empt}}
		\begin{itemize}
			\item Auto-Battle 1 Attack
			\item Wait 32 seconds to end or let Hope end the fight.
		\end{itemize}
		\itemdrop{96}{Fortisol}
	\end{battle}

	\pickup{Fortisol}{beind the Scandroids}
	\begin{menu}
		\begin{itemize}
			\item \textbf{Settings}
			      \begin{itemize}
				      \item Battle Speed: Normal
			      \end{itemize}
		\end{itemize}
	\end{menu}

	\begin{battle}[0:12]{Ghoul x3}
		\itemdrop{12}{Fortisol}
	\end{battle}

	\begin{battle}{Ghoul x2 \textbf{Pre-Empt}}
	\begin{itemize}
	    \item Blitz if both are close, Attack x2 otherwise
	    \item If Attack x2, change targets after Sazh hits one of them to stagger both.
	\end{itemize}
	\end{battle}

	\pickup{Power Wristband}{behind the Ghouls.}
	
		\begin{menu}
		\begin{itemize}
			\item \textbf{Equipment}
			      \begin{itemize}
				      \item Lightning
				            \begin{itemize}
					            \item Optimize: Offensive (Gladius \& Power Wristband)
				            \end{itemize}
			      \end{itemize}
		\end{itemize}
	\end{menu}
	
	Check shrouds. Minimum required 8 Deceptisols/2 Fortisols. Can fight the ghoul blocking the pathway to the rest of the area for a Deceptisol.

	Ghoul hallway is as follows: {\bf Fortisol, Deceptisol, Deceptisol, Fortisol, Deceptisol}

	\begin{battle}[0:41]{Ghoul}
		\begin{itemize}
			\item Wait 41 seconds before attacking or let Sazh finish the battle.
		\end{itemize}
	\end{battle}

	\textbf{Fortisol} on the elevator.

	\begin{battle}[0:54]{Anima}

		\begin{itemize}
		    \item Blitz target the Right Manipulator. Execute on Anima after Snow + Sazh attack it
		    \item Blitz Anima again after swipe
		    \item When the Left Manipulator is dead, hover over the Right Manipulator again, execute on Anima
		    \item Auto-battle until the end of the fight.
		    \item Potion if anyone is red, especially after the arms respawn.
		\end{itemize}
	\end{battle}

	\save{2}

	\save{3}

