\chapter{Mi'ihen Highroad}
\restartlist{enumerate}
\textcolor{red}{From this point until the end of Mushroom Rock Road the encounters can be dangerous. Heal after any ambushes and any time Tidus gets hit.}
\liteversiondetermination{Exclude}{%
\begin{enumerate}
	\item Walk up. Forced encounter, \sd. Walk up, \sd\ during Maechen Scene.
\end{enumerate}
}
\begin{encounters}
	\begin{itemize}
		\item Bomb:
		      \begin{itemize}
			      \switch{anyone}{\kimahri}
			      \kimahrif Lancet Bomb, learn \textbf{Self Destruct}
			      \item Flee.
		      \end{itemize}
		\item Else Flee,  Heal afterwards if it was an ambush.
	\end{itemize}
\end{encounters}
\liteversiondetermination{Exclude}{%
\begin{enumerate}[resume]
	\item {Mi'ihen Skip}
	      \begin{itemize}
		      \item After Maechen Scene, run up as quickly as possible.
		      \item Go to the White Spot on the ground towards the left before the Man in Blue
		      \item Speak to the man, get the \textbf{Hunter's Spear}
		      \item Mash and step forward over the cutscene line
		      \item Walk up during the cutscene after the teleport to the next screen.
	      \end{itemize}
	\item Make sure you get the \textbf{Hunter's Spear} if you fail the skip.
	\item Go right and \sd\ at Calli scene. Continue walking up. \sd\ Luzzu scene, \sd\ Shelinda scene
	\item \formation{\tidus}{\wakka}{\auron}
	\item Go to the next screen
	\item Go to the Al-Bhed shop, \sd. Walk out of the shop and \cs[5:30]
	\item Leave shop, \sd. \sd\ on Rin. Walk outside.
\end{enumerate}
}
\liteversiondetermination{Include}{%
\begin{enumerate}[resume]
	\item Get Hunter's Spear
	\item \formation{\tidus}{\wakka}{\auron} before Chocobo Eater
\end{enumerate}
}
\begin{battle}{Chocobo Eater}
	\begin{itemize}
		\item Defend with everyone.
		\item Swap any characters that fall into crit HP with someone in the back.
	\end{itemize}
\end{battle}
\liteversiondetermination{Exclude}{%
\begin{enumerate}[resume]
	\item \sd
	\item Walk north, \save. \important{Lend O'aka 1100 gil if you didn't give it to him earlier.}
	\item Walk north to next screen. Walk to blocked road, \sd. Speak to the guard on the right, \sd, walk back, \sd. Walk up to next screen.
	\item \textit{If you don't have \textbf{Self Destruct}, make sure that you get it before leaving the second screen.}
\end{enumerate}
}
\liteversiondetermination{Include}{%
\begin{enumerate}[resume]
	\item \important{Lend O'aka 1100 gil if you didn't give it to him earlier.}
\end{enumerate}
}