\chapter{Mushroom Rock Road}
\restartlist{enumerate}
\begin{enumerate}
	\liteversiondetermination{Exclude}{%
	\item \sd, \cs.
	\item Clasko Skip
		\begin{itemize}
			\item Run forward to the 3 Soldiers
			\item Wedge yourself behind the right soldier by holding Left for a second
			\item Tap Down-Right, X to speak to the bottom soldier
			\item If the Soldier got away:
			\begin{itemize}
				\item Run up near the white spot on the wall near the trigger
				\item Talk to the Soldier right after he pushes you into the trigger
				\item Mash until trigger dialogue during the \cs
			\end{itemize}
		\end{itemize}
	}
	\item Flee from all encounters, go to the next screen.
	\item \save. Go up the lift. Follow path.
	\item \formation{\tidus}{\wakka}{\auron}
	\item Early on there is a crusader stood next to a chest, through a rock arch. Open the chest for 1000 Gil
	\item At the end of the first path go up the lift.
	\item Speak to the man immediately ahead of you for an X-Potion
	\item Speak to the man to the left of the next elevator that takes you up to the HQ Elevator, for 400 Gil.
	\item Speak to the man next to the HQ elevator for a Mega-Potion. Go on lift, go to HQ.
	\item Walk down and \sd. Walk right to next screen, then right, \sd. Walk right to O'aka.
	\item Before talking to O'aka:
	\begin{itemize}
		\item Auto-sort Items
		\item \formation{\tidus}{\wakka}{\yuna}
	\end{itemize}
\end{enumerate}
\begin{shop}{10890}
	\begin{itemize}
		\item Sell
			\begin{itemize}
				\item Ethers
				\item X-Potions
				\item Elixirs
				\item Mega-Potions
				\item Hunter's Spear
				\item Anything other than Official Ball, Lightning Steel, Thunder Ball
			\end{itemize}
		\item Buy
			\begin{itemize}
				\item Sentry, Equip
			\end{itemize}
	\end{itemize}
\end{shop}
\liteversiondetermination{Exclude}{%
\begin{enumerate}[resume]
	\item \save
	\item \sd, go right, \cs[1:00], \sd\ after Seymour. Go down to guard, use the \nth{2} option to confirm Yes, \sd
\end{enumerate}
}
\vfill\ \columnbreak
\begin{battle}[12000]{Sinspawn Gui 1}
	\begin{itemize}
		\item If \yuna\ hit by Thunder:
			\begin{itemize}
				\tidusf Switch Weapon to Stunning Steel
				\switch{\yuna}{\auron}
				\auronf Power Break Main Body
				\switch{\wakka}{\kimahri}
				\kimahrif Self Destruct main body
				\switch{\tidus}{\yuna}
				\summon{\valefor}
			\end{itemize}
		\item Otherwise:
			\begin{itemize}
				\switch{\tidus}{\auron}
				\auronf Power Break Main Body
				\yunaf Switch Weapon to Staff
				\switch{\wakka}{\kimahri}
				\kimahrif Self Destruct main body
				\summon{\valefor}
			\end{itemize}
		\valeforf Energy Blast
		\enemyf Attack
		\enemyf Demi
		\valeforf Thunder
		\enemyf Attack / Demi
		\valeforf Thunder
		\enemyf Attack / Demi
		\valeforf Thunder (If HP < 329 and last action was Demi, use shield until gui attacks then use Thunder)
		\valeforf Energy Blast
		\item \textit{If Self Destruct Crit \textit{(3864)}:}
			\begin{itemize}
				\valeforf Energy Blast
				\valeforf Boost
				\valeforf Energy Blast
			\end{itemize}
		\item \textit{If Power Break Failed}
			\begin{itemize}
				\valeforf Energy Blast
				\summon{\ifrit} once \valefor\ dies.
				\ifritf Fire Main Body until 3000 HP
			 	\ifritf Hellfire
			\end{itemize}
	\end{itemize}
\end{battle}
\liteversiondetermination{Exclude}{%
\begin{enumerate}[resume]
	\item \cs+\skippablefmv[2:20]. \sd\ Seymour dialogue.
\end{enumerate}
}
\begin{battle}[6000]{Sinspawn Gui 2}
	\begin{itemize}
		\item \textbf{\textcolor{YellowGreen}{Seymour}}: Thundara Head ($\leftarrow$)
		\item \textbf{\textcolor{YellowGreen}{Seymour}}: Thundara Body x5
		\yunaf Defend
		\auronf Defend
	\end{itemize}
\end{battle}
\liteversiondetermination{Exclude}{%
\begin{enumerate}[resume]
	\item \sd, \cs+\skippablefmv[2:00] (press Start immediately after the skip. Do not use it on the upcoming scenes, as you will crash your game). Walk left and up to Gatta, \sd. \fmv+\cs[1:30], \sd\ during \tidus\ monologue. \cs[1:00], \sd
	\item Walk left, \sd. Walk left, speak to \auron, \sd. \save\ if \auron\ is in critical HP. Go up and right, \sd, exit area, \sd.
\end{enumerate}
\vfill\ \columnbreak
}

