\chapter{Djose}
\restartlist{enumerate}
\begin{enumerate}
	\item Talk to the guard in Burgundy just to the left and get Soft Ring
	\item \formation{\tidus}{\yuna}{\auron}
	\item Walk North.
\end{enumerate}
\begin{encounters}
	\begin{itemize}
		\item Basilisk:
		      \begin{itemize}
			      \switch{anyone}{\kimahri}
			      \kimahrif Lancet Basilisk, learn \textbf{Stone Breath}
			      \item Flee.
		      \end{itemize}
		\item Else Flee
	\end{itemize}
\end{encounters}
\liteversiondetermination{Exclude}{%
\begin{enumerate}[resume]
	\item Continue walking north, \sd, walk up to the next screen.
	\item Walk along bridge to next screen, \sd, walk into temple. Speak to \auron\ at the doorway, \sd, walk up the stairs.
\end{enumerate}
%\vfill
%\ 
%\columnbreak
%\ \newline
\begin{trial}
	\begin{itemize}
		\item Take the sphere from the left wall
		\item Place into door
		\item Take the sphere from the right wall
		\item Place into door
		\item Take the sphere from the left wall
		\item Push pedestal to the right
		\item Put sphere into the far right wall
		\item Take right sphere
		\item Place into the far right wall
		\item \cs
		\item Take sphere from far right wall
		\item Reset puzzle with the far left tile
		\item Place sphere into pedestal
		\item Take the pedestal sphere
		\item Put sphere into right wall
		\item Take the far right sphere
		\item Put into pedestal
		\item Push pedestal through the door
		\item Jump onto pedestal
		\item Push the second pedestal, return to main room
		\item Take the charged sphere from the right wall
		\item Place charged sphere into the left wall
		\item Reset
		\item Place the two pedestal spheres in the first left and right walls
		\item Go onto the lift in the center
		\item Push all the pedestals in, walk up the stairs
	\end{itemize}
\end{trial}
\begin{enumerate}[resume]
	\item Talk to \auron, wait. \sd, try to leave, \sd, name \ixilon
	\item Speak to \auron, enter the temple and go to the left room. Open the chest for a \textbf{Remedy}. Speak to the priest, \sd. Exit the temple, \sd
	\item Go left, \pickup{4000 Gil}
	\item Cross the bridges, \sd, exit, \sd, go up to Moonflow.
\end{enumerate}
}
\liteversiondetermination{Include}{%
\begin{enumerate}[resume]
	\item Do Auron Affection
	\item Don't need Remedy
	\item Grab 4000 Gil Chest outside temple
\end{enumerate}
}