\chapter{Thunder Plains}
\restartlist{enumerate}
\begin{enumerate}
	\liteversiondetermination{Exclude}{\item Walk north, dodging lightning.}
	\item Pray (With Square/X) at the cactuar stone just North of the first Lightning Tower
\end{enumerate}
\begin{encounters}
	\begin{itemize}
		\item Steal the following items from Fiends in the Thunder Plains. Always Flee after Stealing.
		\begin{itemize}
			\item Gold Element / Aerouge: 1x Electro Marble
			\item Larva: 2x Lunar Curtain
			\item Qactuar: 1x Chocobo Feather (Can be stolen later in Bikanel if needed. More are better so steal any extras you can.)
			\item Iron Giant: 2x Light Curtain (Only seen in second half of Thunder Plains)
			\item \textbf{(Optional):} Rare steals from lizards for Petrify Grenades, which can be helpful later
		\end{itemize}
		\vspace{\baselineskip}
		\item On the first Iron Giant Fight Defend with \tidus\ and \auron\ so \rikku\ gets hit then Flee
		\vspace{\baselineskip}
		\item On the second Iron Giant Fight, if \yuna\ needs Overdrive :
			\begin{itemize}
				\switch{\rikku}{\yuna}
				\yunaf attack self
				\tidusf defend
				\switch{\auron}{\rikku}
				\rikkuf steal from Iron Giant
				\item Flee
			\end{itemize}
	\end{itemize}
\end{encounters}
\liteversiondetermination{Exclude}{%
\begin{enumerate}[resume]
	\item \sd\ when approaching Al Bhed shop. Walk into the shop when \rikku\ begs to go inside.
\end{enumerate}
}
\begin{shop}{3400}
	\begin{itemize}
		\item Buy:
			\begin{itemize}
				\item 2x Soft
				\item 11x Grenade
			\end{itemize}
	\end{itemize}
	Check to see if you have at least 6313 Gil after the shop
\end{shop}
\liteversiondetermination{Exclude}{%
\begin{enumerate}[resume]
	\item Walk into shop corridor, \cs[2:00]
	\item Speak to \auron, then to \rikku, \sd.
	\item Pickup the \textbf{Yellow Shield} outside the agency if you had less than 6313 Gil after the shop.
	\item Exit screen, go north, near the exit \sd, \cs[3:10]
\end{enumerate}
\vfill
\ 
\columnbreak
\ \newline
}
\liteversiondetermination{Include}{%
\begin{enumerate}[resume]
	\item Pickup the \textbf{Yellow Shield} outside the agency if you had less than 6313 Gil after the shop.
\end{enumerate}
}