\chapter{Airship}
\restartlist{enumerate}
\liteversiondetermination{Exclude}{%
\begin{enumerate}
	\item \sd\ during \cs\ +3 \skippablefmv. Walk down corridor to the next screen, go back in, \sd. Speak to Brother, \sd. Walk towards corridor, \sd. Walk towards camera to the next screen, go up and speak to Rin.
	\item \save. Make sure that \rikku\ has \od. If she doesn't, you can get encounters on Rin's first screen.
	\item Shop with rin next to the elevator
\end{enumerate}
}
\liteversiondetermination{Include}{%
\begin{enumerate}
	\item Shop with rin next to the elevator
\end{enumerate}
}
\begin{shop}{6186}
	\begin{itemize}
		\item Sell first 2 weapons / armours in inventory except Soft Ring, Sentry \& Claw
		\item Buy \& Equip:
		\begin{itemize}
			\item Shimmering Blade
			\item Devastator
			\item Seeker's Armlet
			\item Seeker's Bracer
		\end{itemize}
	\end{itemize}
\end{shop}
\newpage
\end{multicols}
\begin{battle}[32000]{Evrae}
	The key to this fight is reducing Evrae's health until it is in the window \textcolor{Red}{[11460-11967]}. Once Evrae is in the damage window you need to perform the killing combo blow but it needs to be well timed. You should try to get Evrae into this window before the second Poison Breath. If you fail to get Evrae into this window before the second Poison Breath it is best to tank another Poison Breath and defend for an extra cycle. Once you are confident with the fight you can judge whether you have the time to get her in the window after the Poison Breath.\newline
	\vspace{\baselineskip}
	\textcolor{Red}{There is a rare outcome where \rikku 's Second Mix crits Evrae (9000+ Damage). Evrae will likely have overshot the damage window and in rare cases Evrae may use haste here. If Evrae hastes then recovery is almost impossible and it is very likely game over. If Evrae is below the damage window do not damage her until next poison breath, Hi-Potion Auron and Phoenix Down Rikku if hit by Evrae.}
	\vspace{\baselineskip}
	\begin{itemize}
		\switch{\tidus}{\rikku}
		\rikkuf Mix Grenade + Purple Sphere
		\kimahrif Hi-Potion \auron\ / Phoenix Down \rikku\ if either gets hit, otherwise spam Attacks
		\auronf Spam Attacks
		\rikkuf Steal x2
		\rikkuf Lunar Curtain \auron
		\rikkuf Use Smoke Bomb / Sleeping Powder (Don't use last Smoke Bomb)
		\rikkuf Use Elemental Damage Item(s)
	\end{itemize}
	\vspace{\baselineskip}
	\begin{itemize}
		\enemyf Poison Breath
	\end{itemize}
	\vspace{\baselineskip}
	\begin{itemize}
		\switch{\auron}{\tidus}
		\tidusf Phoenix Down \rikku
		\tidusf Phoenix Down \kimahri
		\item \textbf{Anyone:} Heal Petrification with Al Bhed Potion / Soft
		\rikkuf Mix Lv.1 Key Sphere + Lv.2 Key Sphere
		\switch{\tidus}{\auron}
		\auronf Antidote Self
		\kimahrif Hi-Potion \auron
		\rikkuf Use Water Gem(s) then 1 Smoke Bomb / Sleeping Powder then elemental damage items
		\item Get Evrae into the damage window here. Once she is in the window defend with all until Poison Breath
	\end{itemize}
	\vspace{\baselineskip}
	\begin{itemize}
		\enemyf Poison Breath
	\end{itemize}
	\vspace{\baselineskip}
	\begin{itemize}
		\switch{\auron}{\tidus}
		\tidusf Phoenix Down \rikku
		\tidusf Phoenix Down \kimahri
		\item \kimahri\ / \tidus\ Heal Petrification with Soft
		\rikkuf Use Smoke Bomb
		\item Killing Combo (Make sure \kimahri\ has a turn between both of \rikku 's turns):
		\begin{itemize}
			\rikkuf Use Smoke Bomb / Sleeping Powder \textcolor{Red}{(If Evrae has already Hasted Skip this step)}
			\kimahrif Self Destruct
			\rikkuf Mix Yellow Sphere + Lv.4 Key Sphere
		\end{itemize}
	\end{itemize}
\end{battle}
\newpage
\begin{multicols}{2}
\liteversiondetermination{Exclude}{%
\begin{enumerate}[resume]
	\item \sd, \skippablefmv[3:00] - Press Start immediately after pressing Square/X.
\end{enumerate}
}