\chapter{Baaj Temple}

\begin{enumerate}
	\item Hold O, Down talk to Jecht. \sd \ when \tidus \ wakes up. Swim around rock and to temple.
	\item \cs, hold O, down and right, \cs.
\end{enumerate}
\begin{battle}{Sahagins and Geosgaeno}
	\begin{itemize}
		\item Attack the two Sahagins until dead
		\item \cs[0:30]
		\item Defend until \cs
	\end{itemize}
\end{battle}
\begin{enumerate}[resume]
	\item Heal \tidus \ with Potions. Open options, switch cursor to memory, aeons to short.
	\item \cs, go down and left and go through door. Pickup flint and exit.
	\item Go north and through door. Climb steps to withered bouquet. Go back to the fire in the center. \cs[2:10]
\end{enumerate}
\begin{battle}[1500]{Klikk}
	\begin{itemize}
		\item \tidus: Attack x6, less with Crits
		\item \cs, \sd
		\item \rikku: Grenade x1, Steal x2 Grenades Total, Attack (need at least 6 Grenades for Tros)
		\item \tidus: Attack
		\item Potion if \tidus \ is less than 110 HP
		\item Continue until dead
	\end{itemize}
\end{battle}
\begin{enumerate}[resume]
	\item \cs[2:30]. Talk to \rikku \ for tutorial, \sd
	\item Hold O, down, left. Use circle and move forward.
\end{enumerate}
\begin{encounters}
	\begin{itemize}
		\item Piranha:
		      \begin{itemize}
			      \item Steal Grenades with \rikku \ and Attack with \tidus
		      \end{itemize}
	\end{itemize}
\end{encounters}
\begin{enumerate}[resume]
	\item Swim to \save, swim forward. Circle and right across the station.
\end{enumerate}
\begin{battle}{Piranha}
	\begin{itemize}
		\item \rikku: Steal Grenades from each set
		\item \tidus: Attack
	\end{itemize}
\end{battle}
\begin{enumerate}[resume]
	\item \cs, swim down, swim left. Heal with potions if \rikku\ is  below 250 HP
\end{enumerate}
\begin{battle}[2200]{Tros}
	\begin{itemize}
		\item \rikku: Steal if you had less than 6 grenades
		\item \rikku: Grenade x6
		\item \tidus: Attack x2, Standby otherwise
	\end{itemize}
	Guaranteed 2 Power Spheres, Overkill gives +2 Power Spheres
\end{battle}
\begin{enumerate}[resume]
	\item Swim up to the next screen. \cs, follow red arrow to \cs[0:50]
	\item \sd\ until \tidus \ gets food. \cs[3:00]. Walk to \rikku. \cs[2:30], \sd\ during Al Bhed Dialogue. Don't save.
\end{enumerate}